---
title: "Status Study Report"
author: "Austin van Loon and Srikar Katta"
date: "`r Sys.Date()`"
output: 
  rmdformats::readthedown
---

```{r setup, include=FALSE}
rm(list = ls())
library(tidyverse)
library(zipcodeR)
library(ggvenn)
# remotes::install_github("davidsjoberg/ggsankey")
library(ggsankey)
theme_set(theme_bw() + theme(text = element_text(size = 15)))
knitr::opts_chunk$set(echo = TRUE)
```

```{r helper functions and data}
# prolific codes in surveys were not properly assigned, so manually replace them
participant_code_replacements <- function(x, y) {
  # x is the prolific ID that we use to replace participant codes
  # y is the given participant code
  case_when(
    x == '56e130548b1c33000a388671' ~ 'VATZ46',
    x == '6287f4819c5fc8c4d48cc885' ~ 'AVX9QE',
    x == '601d69a993d94008fb2b25dc' ~ 'YWTGUB',
    x == '650464007006929ee0cd9695' ~ 'ZWTG94',
    x == '614ce6a7a33bac955957f7a6' ~ 'TPZZQA',
    x == '6317511c1dd0acb82cf4b131' ~ 'VQWK3M',
    x == '5e3ae8e5ebfb032f9058ef33' ~ 'KB39HV',
    x == '6554d0515dc2a90a0f6b3ae3' ~ 'VNPHMU',
    x == '5ec59e86c9569f5e8000717b' ~ 'ZN3EYY',
    x == '5ee834d45f0f48129a79b683' ~ 'UGED4M',
    .default = y
  ) %>% return()
}
# drop these participant codes -- clarify _why_ with Austin
participant_code_drops <- c('a43n36','a6punv','84z39x','9eemkf','7wgznu','xx43nc')

# affective numeric values
numeric_affect <- function(x) case_when(
        x == "Very slightly or not at all" ~ 0,
        x == "A little" ~ 1,
        x == "Moderately" ~ 2,
        x == "Quite a bit" ~ 3,
        x == "Extremely" ~ 4, 
        .default = NA)
calculate_affect <- function(x, affect_cols) {
  # x : data frame/tibble
  # affect_cols : list of characters denoting which columns to use
  
  x %>%
    select(paste0('panas_', affect_cols)) %>%
    rowSums(na.rm = TRUE) %>%
    return()
}

get_state_names <- function(x) {
  case_when(x == "AL" ~ "Alabama",
            x == "AK" ~ "Alaska",
            x == "AZ" ~ "Arizona",
            x == "AR" ~ "Arkansas",
            x == "CA" ~ "California",
            x == "CO" ~ "Colorado",
            x == "CT" ~ "Connecticut",
            x == "DE" ~ "Delaware",
            x == "FL" ~ "Florida",
            x == "GA" ~ "Georgia",
            x == "HI" ~ "Hawaii",
            x == "ID" ~ "Idaho",
            x == "IL" ~ "Illinois",
            x == "IN" ~ "Indiana",
            x == "IA" ~ "Iowa",
            x == "KS" ~ "Kansas",
            x == "KY" ~ "Kentucky",
            x == "LA" ~ "Louisiana",
            x == "ME" ~ "Maine",
            x == "MD" ~ "Maryland",
            x == "MA" ~ "Massachusetts",
            x == "MI" ~ "Michigan",
            x == "MN" ~ "Minnesota",
            x == "MS" ~ "Mississippi",
            x == "MO" ~ "Missouri",
            x == "MT" ~ "Montana",
            x == "NE" ~ "Nebraska",
            x == "NV" ~ "Nevada",
            x == "NH" ~ "New Hampshire",
            x == "NJ" ~ "New Jersey",
            x == "NM" ~ "New Mexico",
            x == "NY" ~ "New York",
            x == "NC" ~ "North Carolina",
            x == "ND" ~ "North Dakota",
            x == "OH" ~ "Ohio",
            x == "OK" ~ "Oklahoma",
            x == "OR" ~ "Oregon",
            x == "PA" ~ "Pennsylvania",
            x == "RI" ~ "Rhode Island",
            x == "SC" ~ "South Carolina",
            x == "SD" ~ "South Dakota",
            x == "TN" ~ "Tennessee",
            x == "TX" ~ "Texas",
            x == "UT" ~ "Utah",
            x == "VT" ~ "Vermont",
            x == "VA" ~ "Virginia",
            x == "WA" ~ "Washington",
            x == "WV" ~ "West Virginia",
            x == "WI" ~ "Wisconsin",
            x == "WY" ~ "Wyoming",
            x == "DC" ~  "District of Columbia", 
            x == "PR" ~  "Puerto Rico") %>%
    return()
}
```

# Notes for Austin
- All the 3rd order variables have NA values
- Why do we drop the following codes? `'a43n36','a6punv','84z39x','9eemkf','7wgznu','xx43nc'`
- Survey completion time: we were using `Duration (in seconds)_pre + Duration (in seconds)_post` to calculate survey completion time, but we should be using `intake` and `pretreatment` survey completion times


# Attrition
```{r load attrition data, message = FALSE, warning = FALSE, include = FALSE}
# read raw data
intake <- read_csv("./Status Study 12-12-selected/intake.csv")
pretreat <- read_csv("./Status Study 12-12-selected/pre.csv")
posttreat <- read_csv("./Status Study 12-12-selected/post.csv")

total_n <- nrow(intake)
consent_drop <- intake %>% filter(Consent == 'No, I do NOT consent') %>% nrow()
jive_drop <-
  intake %>% filter((platforms_jive == 'A lot') |
                      (intake.platforms_jive == 'Some')) %>% nrow()
device_drop <- intake %>%
  filter((download_apple == 'No, I am NOT') | (download_android == 'No, I am NOT')) %>%
  nrow()

download_drop <- intake %>%
  filter((download_apple == 'No, I am NOT') | (download_android == 'No, I am NOT')) %>%
  nrow()

image_drop <- intake %>%
  filter(screen_image != 3.0) %>%
  filter(!is.na(screen_image)) %>%
  nrow()

age_drop <- intake %>%
  filter(age < 18) %>%
  filter(!is.na(age)) %>% 
  nrow()

us_drop <- intake %>%
  filter(state == "I do not reside in the United States") %>%
  nrow()

forced_attrit <- consent_drop + jive_drop + device_drop + download_drop + image_drop + age_drop + us_drop

intake_completes <- intake %>%
  filter(!is.na(participant_code))

total_attrit_intake <- total_n - intake_completes - forced_attrit



```

## Attrition through full study
```{r attrition through study, echo=TRUE, message=FALSE, warning=FALSE}

# sankey diagram should have columns x, node, next_x, next_node
nodes <- c(
  'Started intake',
  'Finished intake',
  'Did not finish intake',
  'Dropped during download',
  'Started pre-treat' ,
  'Finished pre-treat' ,
  'Did not finish pre-treat' ,
  'Started post-treat' ,
  'Lost during newsfeed',
  'Finished post-treat')

sankey_df <- tribble(
  ~'start', ~'end', ~'n',
  'Started intake', , total_n,
  'Started intake', 'Finished intake', intake_completes,
  'Started intake', 'Did not finish intake', total_n - intake_completes,
  'Finished intake', 'Dropped during download', attrit_intake_pretreat,
  'Finished intake', 'Started pre-treat', pretreat_n
)



```


# Data Quality Checks
```{r load data, message=FALSE, warning=FALSE, include=FALSE}
# read in intake, pre-treatment, and post-treatment survey responses
intake <- read_csv('./Status Study 12-12-selected/intake.csv') %>%
  # filter(!is.na(participant_code)) %>% # drop participants without a participant code
  mutate(participant_code = participant_code_replacements(PROLIFIC_PID, participant_code)) %>%
  mutate(participant_code = str_to_lower(participant_code))
  
pretreat <- read_csv('./Status Study 12-12-selected/pre.csv') %>%
  mutate(treatment = str_ends(treatment_arm, 'treat'))

posttreat <- read_csv('./Status Study 12-12-selected/post.csv') %>%
  mutate(third_order = rowSums(select(., starts_with('third_order')), na.rm = TRUE)) %>%
  # turn PANAS variables into numbers
  mutate_at(vars(starts_with('panas_')), numeric_affect) %>%
  mutate(panas_neg = calculate_affect(., c('hostile', 'ashamed', 'upset', 'afraid'))) %>%
  mutate(panas_pos = calculate_affect(., c('active', 'attentive', 'alert', 'determined', 'inspired'))) %>%
  mutate(panas = panas_pos - panas_neg)

survey_df <- posttreat %>%
  inner_join(pretreat, by = 'participant_code', suffix = c('_post', '_pre')) %>%
  inner_join(intake %>% filter(!is.na(participant_code)), # drop participants without a participant code
             by = 'participant_code') %>%
  # drop participants in the code drop list
  filter(!(participant_code %in% participant_code_drops)) %>%
  # make a variable for assigned SMA condition
  mutate(condition = case_when(
    str_ends(treatment_arm, 'pc') ~ 'pure_control',
    str_ends(treatment_arm, 'treat') ~ 'treat',
    str_detect(treatment_arm, 'control') ~ 'control',
    .default = NA
  ))

# make a new race variable
survey_df <- survey_df %>% 
  mutate(
    race_new = case_when(
    race == 'Hispanic,White' ~ 'Hispanic',
    race == 'Something else' ~ 'Mixed/other',
    str_count(race, ',') > 0 ~ 'Mixed/other',
    .default = race))

# make a new education variable
survey_df <- survey_df %>% 
  select(participant_code, starts_with('educ_')) %>%
  pivot_longer(cols = starts_with('educ_')) %>%
  filter(!is.na(value)) %>%
  select(-name) %>%
  rename(new_educ = value) %>%
  inner_join(survey_df, by = 'participant_code') 

# convert intellectual humility to numeric
survey_df <- survey_df %>%
  mutate(across(contains('_ih_'), 
                .fns = function(x) {
                  case_match(x,
                            'Not at all well'~ 0,
                            'Not too well'~ 1,
                            'Somewhat well'~ 2,
                            'Very well'~ 3,
                            'Extremely well'~ 4)}
                )
         ) %>%
  rowwise() %>%
  mutate(pre_ih = sum(across(.cols = starts_with('pre_ih_')), na.rm = TRUE),
         post_ih = sum(across(.cols = starts_with('post_ih_')), na.rm = TRUE),
         delta_ih = post_ih - pre_ih,
         pre_ih_binary = pre_ih/6 >= 3)

# calculate affective polarization
survey_df <- survey_df %>%
  mutate(
    same_therm_change = post_therm_1 - pre_therm_1, # change in own party ideals
    diff_therm_change = post_therm_2 - pre_therm_2, # change in out-party feelings,
    affective_polarization = (same_therm_change - diff_therm_change)/100
  )

# calculate moderation of ideals
survey_df <- survey_df %>%
  mutate(across(contains('_policy_'),
                .fns = function(x) case_match(x,
                                              'Strongly agree' ~ 3, 
                                              'Agree' ~ 2,
                                              'Somewhat agree' ~ 1, 
                                              'Neither agree nor disagree' ~ 0, 
                                              'Disagree' ~ 1,
                                              'Somewhat disagree' ~ 2,
                                              'Strongly disagree' ~ 3))) %>%
  mutate(
    extremity_pre = case_when(
      str_detect(treatment_arm, 'gc') ~ pre_policy_gc,
      str_detect(treatment_arm, 'imm') ~ pre_policy_imm
    ),
    extremity_post = case_when(
      str_detect(treatment_arm, 'gc') ~ post_policy_1,
      str_detect(treatment_arm, 'imm') ~ post_policy_2
    ),
    extremity_post_less_pre = extremity_post - extremity_pre
  )

# convert platform descriptions to numeric values
survey_df <- survey_df %>%
  mutate(across(contains('desc_platform_'),
         .fns = function(x) {case_match(x,
                                       "Not at all"~ 1,
                                       "Very little"~ 2,
                                       "Some"~ 3,
                                       "Quite a bit"~ 4,
                                       "A great deal"~ 5,
                                       .default = NA)}))

# convert social media platform usage to numeric
survey_df <- survey_df %>%
  mutate(across(starts_with('platforms_'),
                .fns = function(x) {
                  case_when(
                            x == 'A lot' ~ 2, 
                            x == 'Some' ~ 1, 
                            x == 'Not at all' ~ 0,
                             .default = NA)
                })
         ) %>%
  mutate(social_media_sum = sum(across(.cols = starts_with('platforms_'))), na.rm = TRUE) %>%
  mutate(
         social_media_high  = (social_media_sum >= 5)
         )

```

## Participant Selection
### Survey Completion Time
```{r survey completion time, message=FALSE, warning=FALSE}
survey_df$pretreatment_intake_time <- survey_df$`Duration (in seconds)` + survey_df$`Duration (in seconds)_pre`
survey_df$speeder <- survey_df$pretreatment_intake_time <= median(survey_df$pretreatment_intake_time)/4 %>%
  replace_na(FALSE)
survey_df %>%
  ggplot() +
  geom_histogram(aes(x = pretreatment_intake_time), alpha = 0.5) +
  scale_x_log10() +
  geom_vline( aes(xintercept = median(pretreatment_intake_time)/2, linetype = 'Median/2')) +
  geom_vline( aes(xintercept = median(pretreatment_intake_time)/4, linetype = 'Median/4')) +
  labs(
    x = 'Pre-treatment and intake completion time (in sec)',
    y = 'Count',
    linetype = 'Threshold',
    title = 'Survey Completion Time',
    subtitle = paste0('#Speeders (Time <= Median/4): ', sum(survey_df$speeder))
  )
  
sum(survey_df$pretreatment_intake_time <= median(survey_df$pretreatment_intake_time)/2)
```

## Zip code/state matches
```{r zip code/state matches, message = FALSE, warning = FALSE}
# survey_df$state_from_zip <- 
survey_df <- survey_df %>%
  mutate(zip = case_when(
    nchar(zip) == 4 ~ paste0('0', zip),
    .default = zip
  ))


survey_df <- zip_code_db %>%
  select(zipcode, state) %>%
  rename(zip_state = state) %>%
  right_join(survey_df, by = c('zipcode' = 'zip')) %>%
  mutate(
    zip_state = 
      case_when(
        zipcode == '77407' ~ "TX",
        zipcode == '85756' ~ "AZ",
        zipcode == '49519' ~ "MI",
        zipcode == "34638" ~ "FL",
        zipcode == "25405" ~ "WV",
        zipcode == "10065" ~ "NY",
        zipcode == "89183" ~ "NV",
        zipcode == "89178" ~ "NV",
        zipcode == "85143" ~ "AZ",
        zipcode == "85140" ~ "AZ",
        zipcode == "32163" ~ "FL",
        zipcode == "85119" ~ "AZ",
        zipcode == "29486" ~ "SC",
        zipcode == "85142" ~ "AZ",
        zipcode == "60169" ~ "IL",
        zipcode == "98391" ~ "WA",
        zipcode == "80923" ~ "CO",
        # https://researchmaniacs.com/ZipCodes/4/Where-is-Zip-Code-46907.html
        zipcode == "46907" ~ "IN",
        zipcode == "10486" ~ "NY",
        zipcode == "91760" ~ "CA",
        zipcode == "00000" ~ NA,
        zipcode == "46343" ~ "IN",
        zipcode == "90289" ~ "CA",
        zipcode == "90268" ~ "CA",
        .default = zip_state)
  ) %>%
  mutate(state_full = get_state_names(zip_state))

survey_df <- survey_df %>%
  mutate(pass_zip_check = (survey_df$state_full == survey_df$state)) %>%
  mutate(pass_zip_check = replace_na(pass_zip_check, replace = FALSE))


```

### Bonus word check
```{r bonus check, echo=FALSE, message=FALSE, warning=FALSE}
survey_df$correct_bonus <- survey_df$password %>%
  str_to_lower() %>%
  str_detect('win') %>%
  replace_na(FALSE)
```

```{r venn diagram, message = FALSE, warning = FALSE, echo = FALSE}
ggplot(survey_df) +
  geom_venn(aes(A = !speeder, B = pass_zip_check, C = correct_bonus), show_percentage = FALSE,
            set_names = c('Did not speed', 'Zip code state = Reported state', 'Correct bonus word'),
            fill_color = c('#3b528b', '#21918c', '#5ec962')) +
  scale_fill_viridis_b() +
  theme_classic() +
  theme(axis.text.x=element_blank(), 
      axis.ticks.x=element_blank(), 
      axis.text.y=element_blank(), 
      axis.ticks.y=element_blank(),
      axis.line.x = element_blank(),
      axis.line.y = element_blank()) 
```
```{r participant check, message = FALSE, warning = FALSE, echo = FALSE}
survey_df %>%
  group_by(!speeder, pass_zip_check, correct_bonus) %>%
  count() %>%
  rename(`Did not speed` = `!speeder`,
         `Zip code state = Reported state` = pass_zip_check,
         `Correct bonus word` = correct_bonus) %>%
  pander::pander()
```


## Demographic/Balance checks
### Age
```{r demog and balance checks, echo=FALSE, message=FALSE, warning=FALSE}

demogs_plot <- function(col, factor_list = NULL, title = NA) {
  if(!is.null(factor_list)) {
    survey_df <- survey_df %>%
      mutate_at(.vars = c(col), .funs = function(x) factor(x, levels = factor_list))
  }
  if(col == 'age') {
  p <- ggplot(survey_df) +
      geom_histogram(aes_string(x = col, fill = 'condition'), position = 'identity', alpha = 0.5, stat = 'count') 
  p_value <- min(ks.test(survey_df[survey_df$condition == 'treat', ]$age,
                         survey_df[survey_df$condition == 'control', ]$age)$p.value,
                 ks.test(survey_df[survey_df$condition == 'treat', ]$age,
                         survey_df[survey_df$condition == 'pure_control',]$age)$p.value,
                 ks.test(survey_df[survey_df$condition == 'pure_control',]$age,
                         survey_df[survey_df$condition == 'control',]$age)$p.value
                 )
  }
  else {
    p <- ggplot(survey_df) +
      geom_histogram(aes_string(x = col, fill = 'condition'), position = 'dodge2', stat = 'count')
    p_value <- survey_df %>% 
      group_by(condition, (!!as.symbol(col))) %>% 
      count() %>% 
      pivot_wider(id_cols = 'condition', names_from = col, values_from = 'n') %>%
      ungroup() %>%
      column_to_rownames('condition') %>%
      as.matrix() %>%
      chisq.test() %>%
      .$p.value
  }
  p <- p +
    theme(legend.position = 'bottom',
          axis.text.x = element_text(angle = 45, hjust = 1)) +
    labs(title = paste0('Histogram of `', title, '`'),
         subtitle = paste0('#Missing values: ', is.na(survey_df[col]) %>% sum()),
         caption = paste0('Min p-value from KS/Chi^2 test between groups: ', round(p_value, 4)),
         x = title)
  return(p)
}

demogs_plot('age', title = 'Age')
demogs_plot('pid3', c('Democrat', 'Independent', 'Republican', 'Other'), title = 'Political Identity')
demogs_plot('ideo7', 
            c('Extremely liberal', 'Liberal', 'Somewhat liberal', 'Moderate or middle of the road', 'Somewhat conservative', 'Conservative', 'Extremely conservative'),
            'Ideology')

demogs_plot('new_educ', c('Less than high school', 
                          'High school graduate or equivalent (GED)',
                          'Some college but no degree',
                          'Associate degree in college',
                          'Bachelor’s degree',
                          'Post-graduate degree'),
            'Education')
```
# Attrition Checks
```{r attrition, echo=FALSE, include=FALSE, warnings=FALSE, error=FALSE}
intake_w_nas <- read_csv('./Status Study 12-12-selected/intake.csv') %>%
  mutate(participant_code = participant_code_replacements(PROLIFIC_PID, participant_code)) %>%
  mutate(participant_code = str_to_lower(participant_code))
pretreat_w_nas <- read_csv('./Status Study 12-12-selected/pre.csv')
posttreat_w_nas <- read_csv('./Status Study 12-12-selected/post.csv')



intake_w_nas %>%
  mutate(consent_drop = (Consent == 'No, I do NOT consent'),
         jive_drop = (platforms_jive == 'A lot') | (platforms_jive == 'Some'),
         device_drop = device == 'Something else',
         download_drop = (download_apple == 'No, I am NOT') | (download_android == 'No, I am NOT'),
         image_drop = (screen_image != 3),
         age_drop = (age < 18),
         us_drop = (state == 'I do not reside in the United States'),
         intake_complete = !is.na(participant_code)) %>%
  group_by(across(ends_with('_drop'))) %>%
  count() %>%
  ungroup() %>%
  pivot_longer(cols = -n) %>%
  filter(!is.na(value))

```



# Main Hypothesis Tests
```{r main ttest code, message=FALSE, warning=FALSE}
main_hypothesis_test <- function(df,
                                 outcome,
                                 main_condition = 'treat',
                                 contrast_condition = 'control',
                                 display_plot = FALSE,
                                 title = '',
                                 return_object = FALSE) {
  # isolate data for main group and contrast group
  outcome_main_group <- df %>%
    filter(condition == main_condition) %>% 
    .[outcome] %>% 
    drop_na() %>% 
    pull(.)
  
  outcome_contrast_group <- df %>% 
    filter(condition == contrast_condition) %>% 
    .[outcome] %>% 
    drop_na() %>% 
    pull(.)
  
  # run t test comparing these two groups
  ttest_results <- t.test(
    x = outcome_main_group,
    y = outcome_contrast_group,
    alternative = 'two.sided',
    var.equal = FALSE
  )
  # ttest_estimate <- ttest_results$
  ttest_pvalue <- ttest_results$p.value
  ttest_cohens_d <- effsize::cohen.d(outcome_main_group,
                                     outcome_contrast_group)$estimate
  
  # make ttest plot
  n_stars <- ''
  if(ttest_pvalue < 0.05) { n_stars <- '*'}
  else if(ttest_pvalue < 0.01) { n_stars <- '**'}
  else if(ttest_pvalue < 0.001) { n_stars <- '***' }
  p <- ggplot() +
    geom_bar(aes(x = outcome_main_group, y = ..prop.., fill = main_condition), alpha = 0.5, position = 'identity') +
    geom_bar(aes(x = outcome_contrast_group, y = ..prop.., fill = contrast_condition), alpha = 0.5, position = 'identity') +
    geom_density(aes(x = outcome_main_group, fill = main_condition), alpha = 0.5, position = 'identity') +
    geom_density(aes(x = outcome_contrast_group, fill = contrast_condition), alpha = 0.5, position = 'identity') +
    geom_vline(aes(xintercept = mean(outcome_main_group), linetype = main_condition), linewidth = 1) +
    geom_vline(aes(xintercept = mean(outcome_contrast_group), linetype = contrast_condition), linewidth = 1) +
    labs(x = outcome,
         y = 'density',
         title = paste0(title, ': ', outcome, n_stars),
         subtitle = paste0('(p=', round(ttest_pvalue, 3), ', D=', round(ttest_cohens_d, 3), ')'),
         fill = 'Contrast groups',
         linetype = 'Contrast groups'
         )
  
  if(ttest_pvalue < 0.05) {
    p <- p + 
      theme(plot.title = element_text(face = 'bold'),
            plot.subtitle = element_text(face = 'bold'))
  }
return_list <- list('contrast' = paste(main_condition, 'vs', contrast_condition),
                    'ttest' = ttest_results,
                    'p.value' = ttest_pvalue,
                    'cohen.d' = ttest_cohens_d,
                    'plot' = p)
  # if you should display the plot, make the plot and display it
  if(display_plot) print(p)
  if(return_object) return(return_list)
}

subgroup_hypothesis_test <- function(df,
                                 outcome,
                                 subgroup_col,
                                 subgroup_rhs,
                                 main_condition = 'treat',
                                 contrast_condition = 'control',
                                 display_plot = FALSE,
                                 title = '',
                                 return_object = FALSE) {
  result <- main_hypothesis_test(
    df %>% filter(.data[[subgroup_col]] == subgroup_rhs),
    outcome,
    main_condition,
    contrast_condition,
    display_plot,
    title = paste0(title, subgroup_col, '=', subgroup_rhs),
    return_object = TRUE
  )
  if (return_object) return(result)
}

subgroup_cols <- c('pre_ih_binary',
                   'pre_ih_binary',
                   'social_media_high',
                   'social_media_high',
                   'pid3',
                   'pid3')
subgroup_rhss <- list(1, 0, 1, 0, 'Democrat', 'Republican')

multiple_subgroups_htest <- function(df,
                                 outcome,
                                 subgroup_cols,
                                 subgroup_rhss,
                                 main_condition = 'treat',
                                 contrast_condition = 'control',
                                 display_plot = FALSE,
                                 title = '',
                                 return_object = FALSE) 
  {
  row_names <- paste0(subgroup_cols, '=', subgroup_rhss)
  subgroup_results <- data.frame('contrast' = rep(NA, length(row_names)),
                                 'ttest' = rep(NA, length(row_names)),
                                 'p.value' = rep(NA, length(row_names)),
                                 'cohen.d' = rep(NA, length(row_names)),
                                 'plot' = rep(NA, length(row_names)),
                                 row.names = paste0(subgroup_cols, '=', subgroup_rhss))
  for(index in 1:length(subgroup_cols)) {
    sg_result <- subgroup_hypothesis_test(survey_df,
                           outcome = outcome,
                           subgroup_col = subgroup_cols[index],
                           subgroup_rhs = subgroup_rhss[index],
                           display_plot = display_plot,
                           return_object = TRUE)
    subgroup_results[paste0(subgroup_cols[index], '=', subgroup_rhss[index]), ] <- sg_result
  }
  subgroup_results$outcome <- outcome
  subgroup_results$subgroup <- rownames(subgroup_results)
  rownames(subgroup_results) <- NULL
  if(return_object) return(subgroup_results)
}
```



## Hypothesis 1A: experience less negative emotions
```{r h1a, echo=FALSE, warning=FALSE}
main_hypothesis_test(survey_df, 'panas_neg', display_plot = TRUE, title = 'All participants', return_object = FALSE)
```

## Hypothesis 1B: experience more positive emotions
```{r h1b, echo=FALSE, warning=FALSE}
main_hypothesis_test(survey_df, 'panas_pos', display_plot = TRUE, title = 'All participants', return_object = FALSE)
```

## Hypothesis 1C: experience more positive and less negative emotions
```{r h1c, echo=FALSE, warning=FALSE}
main_hypothesis_test(survey_df, 'panas', display_plot = TRUE, title = 'All participants', return_object = FALSE)
```

## Hypothesis 2: report greater increases in their intellectual humility
```{r h2, echo=FALSE, warning=FALSE}
main_hypothesis_test(survey_df, 'delta_ih', display_plot = TRUE, title = 'All participants', return_object = FALSE)
```

## Hypothesis 3: produce more intellectually humble content

## Hypothesis 4: engage more with intellectually humble content

## Hypothesis 5: experience a greater reduction in their affective polarization
```{r h5, echo=FALSE, warning=FALSE}
main_hypothesis_test(survey_df, 'affective_polarization', display_plot = TRUE, title = 'All participants', return_object = FALSE)
```

## Hypothesis 6: moderate their issue positions to a greater degree
```{r h6, echo=FALSE, warning=FALSE}
main_hypothesis_test(survey_df, 'extremity_post_less_pre', display_plot = TRUE, title = 'All participants', return_object = FALSE)
```


## Subgroup Analyses
```{r echo=TRUE, warning=FALSE}

subgroup <- lapply(X = list('panas_neg', 'panas_pos', 'panas', 'delta_ih', 'affective_polarization', 'extremity_post_less_pre'),
       function(x) multiple_subgroups_htest(
  df = survey_df,
  outcome = x,
  subgroup_cols = c(
    'pre_ih_binary',
    'pre_ih_binary',
    'social_media_high',
    'social_media_high',
    'pid3',
    'pid3'
  ),
  subgroup_rhss = list(1, 0, 1, 0, 'Democrat', 'Republican'),
  main_condition = 'treat',
  contrast_condition = 'control',
  display_plot = FALSE,
  title = '',
  return_object = TRUE
)) %>%
  bind_rows()

subgroup %>%
  filter(p.value <= 0.05) %>%
  select(p.value, cohen.d, outcome, subgroup) %>%
  mutate(stars = case_when(
    p.value <= 0.001 ~ '***',
    p.value <= 0.01 ~ '**',
    p.value <= 0.05 ~ '*'
  )) %>%
  mutate(cohen.d = paste0(round(cohen.d, 3), stars)) %>%
  pivot_wider(id_cols = 'subgroup', names_from = 'outcome', values_from = 'cohen.d') %>%
  column_to_rownames('subgroup') %>%
  pander::pander(caption = 'Rows represent subgroups, columns represent outcome, and entries represent effect size. p<0.05*, p<0.01**, p<0.001***')
```




















