---
title: "Status Study Report"
author: "Austin van Loon and Srikar Katta"
date: "`r Sys.Date()`"
output: 
  rmdformats::readthedown
---

```{r setup, include=FALSE}
rm(list = ls())
library(tidyverse)
library(zipcodeR)
library(ggvenn)
library(tokenizers)
library(networkD3)
library(webshot)
library(vader)

theme_set(theme_bw() + theme(text = element_text(size = 15)))
knitr::opts_chunk$set(echo = TRUE)
```

```{r helper functions and data}
# prolific codes in surveys were not properly assigned, so manually replace them
participant_code_replacements <- function(x, y) {
  # x is the prolific ID that we use to replace participant codes
  # y is the given participant code
  case_when(
    x == '56e130548b1c33000a388671' ~ 'VATZ46',
    x == '6287f4819c5fc8c4d48cc885' ~ 'AVX9QE',
    x == '601d69a993d94008fb2b25dc' ~ 'YWTGUB',
    x == '650464007006929ee0cd9695' ~ 'ZWTG94',
    x == '614ce6a7a33bac955957f7a6' ~ 'TPZZQA',
    x == '6317511c1dd0acb82cf4b131' ~ 'VQWK3M',
    x == '5e3ae8e5ebfb032f9058ef33' ~ 'KB39HV',
    x == '6554d0515dc2a90a0f6b3ae3' ~ 'VNPHMU',
    x == '5ec59e86c9569f5e8000717b' ~ 'ZN3EYY',
    x == '5ee834d45f0f48129a79b683' ~ 'UGED4M',
    .default = y
  ) %>% return()
}
# drop these participant codes -- clarify _why_ with Austin
participant_code_drops <- c('a43n36','a6punv','84z39x','9eemkf','7wgznu','xx43nc')

# affective numeric values
numeric_affect <- function(x) case_when(
        x == "Very slightly or not at all" ~ 0,
        x == "A little" ~ 1,
        x == "Moderately" ~ 2,
        x == "Quite a bit" ~ 3,
        x == "Extremely" ~ 4, 
        .default = NA)
calculate_affect <- function(x, affect_cols) {
  # x : data frame/tibble
  # affect_cols : list of characters denoting which columns to use
  
  x %>%
    select(paste0('panas_', affect_cols)) %>%
    rowSums(na.rm = TRUE) %>%
    return()
}

get_state_names <- function(x) {
  case_when(x == "AL" ~ "Alabama",
            x == "AK" ~ "Alaska",
            x == "AZ" ~ "Arizona",
            x == "AR" ~ "Arkansas",
            x == "CA" ~ "California",
            x == "CO" ~ "Colorado",
            x == "CT" ~ "Connecticut",
            x == "DE" ~ "Delaware",
            x == "FL" ~ "Florida",
            x == "GA" ~ "Georgia",
            x == "HI" ~ "Hawaii",
            x == "ID" ~ "Idaho",
            x == "IL" ~ "Illinois",
            x == "IN" ~ "Indiana",
            x == "IA" ~ "Iowa",
            x == "KS" ~ "Kansas",
            x == "KY" ~ "Kentucky",
            x == "LA" ~ "Louisiana",
            x == "ME" ~ "Maine",
            x == "MD" ~ "Maryland",
            x == "MA" ~ "Massachusetts",
            x == "MI" ~ "Michigan",
            x == "MN" ~ "Minnesota",
            x == "MS" ~ "Mississippi",
            x == "MO" ~ "Missouri",
            x == "MT" ~ "Montana",
            x == "NE" ~ "Nebraska",
            x == "NV" ~ "Nevada",
            x == "NH" ~ "New Hampshire",
            x == "NJ" ~ "New Jersey",
            x == "NM" ~ "New Mexico",
            x == "NY" ~ "New York",
            x == "NC" ~ "North Carolina",
            x == "ND" ~ "North Dakota",
            x == "OH" ~ "Ohio",
            x == "OK" ~ "Oklahoma",
            x == "OR" ~ "Oregon",
            x == "PA" ~ "Pennsylvania",
            x == "RI" ~ "Rhode Island",
            x == "SC" ~ "South Carolina",
            x == "SD" ~ "South Dakota",
            x == "TN" ~ "Tennessee",
            x == "TX" ~ "Texas",
            x == "UT" ~ "Utah",
            x == "VT" ~ "Vermont",
            x == "VA" ~ "Virginia",
            x == "WA" ~ "Washington",
            x == "WV" ~ "West Virginia",
            x == "WI" ~ "Wisconsin",
            x == "WY" ~ "Wyoming",
            x == "DC" ~  "District of Columbia", 
            x == "PR" ~  "Puerto Rico") %>%
    return()
}
```

# Notes for Austin
- Why do we drop the following codes? `'a43n36','a6punv','84z39x','9eemkf','7wgznu','xx43nc'`
- Survey completion time: we were using `Duration (in seconds)_pre + Duration (in seconds)_post` to calculate survey completion time, but we should be using `intake` and `pretreatment` survey completion times
- Gold star $n$: 835
- There are three duplicate `participant_code`s in the `posttreat` survey


# Data Quality Checks
```{r load survey data, message=FALSE, warning=FALSE, include=FALSE}
# read in intake, pre-treatment, and post-treatment survey responses
intake <- read_csv('./Status Study 12-12-selected/intake.csv') %>%
  # filter(!is.na(participant_code)) %>% # drop participants without a participant code
  mutate(participant_code = participant_code_replacements(PROLIFIC_PID, participant_code)) %>%
  mutate(participant_code = str_to_lower(participant_code))

pretreat <- read_csv('./Status Study 12-12-selected/pre.csv') %>%
  mutate(treatment = str_ends(treatment_arm, 'treat'))

posttreat <- read_csv('./Status Study 12-12-selected/post.csv') %>%
  # turn PANAS variables into numbers
  mutate_at(vars(starts_with('panas_')), numeric_affect) %>%
  mutate(panas_neg = calculate_affect(., c('hostile', 'ashamed', 'upset', 'afraid'))) %>%
  mutate(panas_pos = calculate_affect(., c('active', 'attentive', 'alert', 'determined', 'inspired'))) %>%
  mutate(panas = panas_pos - panas_neg)


intake_new <- intake
pretreat_new <- pretreat
posttreat_new <- posttreat

# make a new race variable
intake_new <- intake_new %>%
  mutate(
    race_new = case_when(
      race == 'Hispanic,White' ~ 'Hispanic',
      race == 'Something else' ~ 'Mixed/other',
      str_count(race, ',') > 0 ~ 'Mixed/other',
      .default = race))

# make a new education variable
intake_new <- intake_new %>%
  # ResponseId is unique ID for intake survey
  select(ResponseId, starts_with('educ_')) %>% 
  pivot_longer(cols = starts_with('educ_')) %>%
  filter(!is.na(value)) %>%
  select(-name) %>%
  rename(new_educ = value) %>%
  right_join(intake_new, by = 'ResponseId')

# convert social media platform usage to numeric
intake_new <- intake_new %>%
  mutate(across(.cols = starts_with('platforms_'),
                .fns = 
                  ~case_match(.,
                    'A lot' ~ 2,
                    'Some' ~ 1,
                    'Not at all' ~ 0,
                    .default = NA)
                )
  ) %>%
  rowwise() %>%
  mutate(social_media_sum = sum(across(.cols = starts_with('platforms_')), na.rm = TRUE)) %>%
  # mutate(social_media_sum = . %>% select(starts_with('platforms_')) %>% rowSums(., na.rm = TRUE))
  mutate(
    social_media_high  = (social_media_sum >= 5)
  )

# calculate 7 point political ID
intake_new <- intake_new %>%
  rowwise() %>%
  mutate(pid7 = case_when(
    pid3 %in% c('Other', 'Independent') ~ case_when(
      pid_lean == "Closer to Republican Party" ~ "Lean Republican",
      pid_lean == 'Closer to Democratic Party' ~ "Lean Democrat",
      pid_lean == "Neither" ~ "True Independent/Other",
      .default = "N/A"
    ),
    pid3 == "Republican" ~ case_when(
      pid_strong == "Not very strong ${q://QID41/ChoiceGroup/SelectedChoices}" ~ "Weak Republican",
      pid_strong == 'Strong ${q://QID41/ChoiceGroup/SelectedChoices}' ~ "Strong Republican",
      .default = "N/A"
    ),
    pid3 == "Democrat" ~ case_when(
      pid_strong == "Not very strong ${q://QID41/ChoiceGroup/SelectedChoices}" ~ "Weak Democrat",
      pid_strong == 'Strong ${q://QID41/ChoiceGroup/SelectedChoices}' ~ "Strong Democrat",
      .default = "N/A"
    ),
    .default = as.character(pid3)
  )) %>%
  mutate(pid7_num = case_when(
    pid3 %in% c('Other', 'Independent') ~ case_when(
      pid_lean == "Closer to Republican Party" ~ 1,
      pid_lean == 'Closer to Democratic Party' ~ -1,
      pid_lean == "Neither" ~ 0,
      .default = NA
    ),
    pid3 == "Republican" ~ case_when(
      pid_strong == "Not very strong ${q://QID41/ChoiceGroup/SelectedChoices}" ~ 2,
      pid_strong == 'Strong ${q://QID41/ChoiceGroup/SelectedChoices}' ~ 3,
      .default = NA
    ),
    pid3 == "Democrat" ~ case_when(
      pid_strong == "Not very strong ${q://QID41/ChoiceGroup/SelectedChoices}" ~ -2,
      pid_strong == 'Strong ${q://QID41/ChoiceGroup/SelectedChoices}' ~ -3,
      .default = NA
    ),
    .default = 0
  )) %>%
  mutate(leaner = case_when(pid7_num > 0 ~ 'Republican',
                            pid7_num < 0 ~ 'Democrat',
                            .default = 'Independent'))

# convert intellectual humility to numeric
pretreat_new <- pretreat_new %>%
  mutate(across(contains('_ih_'),
                .fns = ~case_match(.,
                             'Not at all well'~ 0,
                             'Not too well'~ 1,
                             'Somewhat well'~ 2,
                             'Very well'~ 3,
                             'Extremely well'~ 4)
  )
  ) %>%
  rowwise() %>%
  mutate(pre_ih = sum(across(.cols = starts_with('pre_ih_')), na.rm = TRUE),
         pre_ih_binary = pre_ih/6 >= 3)

# calculate moderation of ideals
pretreat_new <- pretreat_new %>%
  mutate(across(contains('_policy_'),
                .fns = ~case_match(.,
                                  'Strongly agree' ~ 3,
                                  'Agree' ~ 2,
                                  'Somewhat agree' ~ 1,
                                  'Neither agree nor disagree' ~ 0,
                                  'Disagree' ~ 1,
                                  'Somewhat disagree' ~ 2,
                                  'Strongly disagree' ~ 3))) %>%
  mutate(
    extremity_pre = case_when(
      str_detect(treatment_arm, 'gc') ~ pre_policy_gc,
      str_detect(treatment_arm, 'imm') ~ pre_policy_imm
    ),
    pre_policy_gc_binary = (pre_policy_gc >= 1.5),
    pre_policy_imm_binary = (pre_policy_imm >= 1.5)
  )


posttreat_new <- posttreat_new %>%
  mutate(across(contains('_ih_'),
                .fns = 
                  ~case_match(.,
                             'Not at all well'~ 0,
                             'Not too well'~ 1,
                             'Somewhat well'~ 2,
                             'Very well'~ 3,
                             'Extremely well'~ 4)
  )
  ) %>%
  rowwise() %>%
  mutate(post_ih = sum(across(.cols = starts_with('post_ih_')), na.rm = TRUE))

# convert future usage
posttreat_new <- posttreat_new %>%
  mutate(future_use_n = case_match(future_use,
                                   'Very unlikely' ~ 1,
                                   'Somewhat unlikely' ~ 2,
                                   'Neither unlikely nor likely' ~ 3,
                                   'Somewhat likely' ~ 4,
                                   'Very likely' ~ 5,
                                   NA ~ NA))

# convert platform descriptions to numeric values

posttreat_new <- posttreat_new %>%
  mutate(engaging = case_match(desc_platform_engaging,
            'Not at all' ~ 5,
            'Very little' ~ 4,
            'Some' ~ 3,
            'Quite a bit' ~ 2,
            'A great deal' ~ 1,
            NA ~ NA),
         toxic = case_match(desc_platform_toxic,
            'Not at all' ~ 1,
            'Very little' ~ 2,
            'Some' ~ 3,
            'Quite a bit' ~ 4,
            'A great deal' ~ 5,
            NA ~ NA),
         exhausting = case_match(desc_platform_exhausting,
            'Not at all' ~ 1,
            'Very little' ~ 2,
            'Some' ~ 3,
            'Quite a bit' ~ 4,
            'A great deal' ~ 5,
            NA ~ NA)) %>%
  rowwise() %>%
  mutate(platforms = mean(c(engaging, toxic, exhausting), na.rm = TRUE))

posttreat_new <- posttreat_new %>%
  mutate(polite = case_match(desc_users_polite,
            'Not at all' ~ 5,
            'Very little' ~ 4,
            'Some' ~ 3,
            'Quite a bit' ~ 2,
            'A great deal' ~ 1,
            NA ~ NA),
         aggressive = case_match(desc_users_aggressive,
            'Not at all' ~ 1,
            'Very little' ~ 2,
            'Some' ~ 3,
            'Quite a bit' ~ 4,
            'A great deal' ~ 5,
            NA ~ NA),
         tolerant = case_match(desc_users_tolerant,
            'Not at all' ~ 1,
            'Very little' ~ 2,
            'Some' ~ 3,
            'Quite a bit' ~ 4,
            'A great deal' ~ 5,
            NA ~ NA)) %>%
  rowwise() %>%
  mutate(users = mean(c(polite, aggressive, tolerant), na.rm = TRUE),
         users_b = mean(c(polite, tolerant), na.rm = TRUE))

posttreat_new <- posttreat_new %>%
  mutate(comfort = case_match(comfort_sharing,
                              "Not at all comfortable" ~ 1,
                               "Slightly comfortable" ~ 2,
                               "Moderately comfortable" ~ 3,
                               "Very comfortable" ~ 4,
                               "Extremely comfortable" ~ 5,
                               NA ~ NA))

posttreat_new <- posttreat_new %>%
    mutate(across(contains('_policy_'),
                .fns = ~case_match(.,
                                  'Strongly agree' ~ 3,
                                  'Agree' ~ 2,
                                  'Somewhat agree' ~ 1,
                                  'Neither agree nor disagree' ~ 0,
                                  'Disagree' ~ 1,
                                  'Somewhat disagree' ~ 2,
                                  'Strongly disagree' ~ 3)))

survey_df_new <- posttreat_new %>%
  inner_join(pretreat_new, by = 'participant_code', suffix = c('_post', '_pre')) %>%
  inner_join(intake_new %>% filter(!is.na(participant_code)), # drop participants without a participant code
             by = 'participant_code') %>%
  # drop participants in the code drop list
  filter(!(participant_code %in% participant_code_drops)) %>%
  # make a variable for assigned SMA condition
  mutate(condition = case_when(
    str_ends(treatment_arm, 'pc') ~ 'pure_control',
    str_ends(treatment_arm, 'treat') ~ 'treat',
    str_detect(treatment_arm, 'control') ~ 'control',
    .default = NA
  )) %>%
  mutate(delta_ih = post_ih - pre_ih) %>%
  mutate(ingroup_therm_pre = (leaner == Party1) * pre_therm_1 + (leaner != Party1) * pre_therm_2,
         outgroup_therm_pre = (leaner == Party1) * pre_therm_2 + (leaner != Party1) * pre_therm_1) %>%
  mutate(ingroup_therm_pre = ifelse(leaner %in% c('Democrat', 'Republican'), ingroup_therm_pre, NA),
         outgroup_therm_pre = ifelse(leaner %in% c('Democrat', 'Republican'), outgroup_therm_pre, NA)) %>%
  mutate(ingroup_therm_post = (leaner == Party1_post) * post_therm_1 + (leaner != Party1_post) * post_therm_2,
         outgroup_therm_post = (leaner == Party1_post) * post_therm_2 + (leaner != Party1_post) * post_therm_1) %>%
  mutate(ingroup_therm_post = ifelse(leaner %in% c('Democrat', 'Republican'), ingroup_therm_post, NA),
         outgroup_therm_post = ifelse(leaner %in% c('Democrat', 'Republican'), outgroup_therm_post, NA)) %>%
  mutate(outgroup_therm_change = outgroup_therm_post - outgroup_therm_pre,
         ingroup_therm_change = ingroup_therm_post - ingroup_therm_pre,
         therm_diff_pre = (ingroup_therm_pre - outgroup_therm_pre)/100, # pre treatment polarization : how different are in group and out group views?
         affective_polarization = (ingroup_therm_change - outgroup_therm_change)/100) %>%
  mutate(pid_extremity = abs(pid7_num)) %>%
  mutate(
    extremity_post = case_when(
      str_detect(treatment_arm, 'gc') ~ post_policy_1,
      str_detect(treatment_arm, 'imm') ~ post_policy_2
    ),
    extremity_post_less_pre = extremity_post - extremity_pre
  ) %>%
  mutate(mc_correct_treat = (condition == 'treat') * (manip_check == 'The degree to which users respectfully engage with and learn from differing opinions.'),
         mc_correct_control = (condition == 'control') * (manip_check == 'The degree to which the user is "popular", or the degree to which they are able to achieve "likes".'),
         mc_correct_pure_control = (condition == 'pure_control') * (manip_check == 'There were no user badges on the platform.')) %>%
  mutate(mc_correct = mc_correct_treat + mc_correct_control + mc_correct_pure_control)

survey_df <- survey_df_new

```

```{r load engagement data, message = FALSE, warning = FALSE, include = FALSE}
ih_posts <- c(
  "A lot of reporting I've seen suggests that the illegal crossing are very dangerous. If that's true, we should do everything we can to deter this. I've heard that many die every year crossing in unsafe areas, and that even when they make it across they die of heat and thrust or crammed in the back of trucks. It seems like, then, a border wall is for their safety as well as ours.",
            "I get the reason some people want gun control.  I want them to understand that where I live, we need guns. We are over run with coyotes. They kill our pets. We try and kill them. You have to use a weapon with range. What youd call an assault weapon is perfect for that, and they are popular here for coyotes. I just scare them with my gun, because I don't ever hit them",
            "I might be wrong but it seems like the places that have the most mayhem are those with the most restrictive laws. I think about the pressure cooker bombs a few years back at the marathon.",
            "I totally understand, it's not the guns fault. We shouldn't do away with guns because of recent incidents, but it seems to me that we need to look at those who use the guns. I think regulating who can get access to them could help solve this issue. I agree that people have the need to feel safe and they should secure their environment the way they feel comfortable",
            "I try not to be naive that utopia exists or can exist. I know some people think differently, but I do believe in laws and rules and that people are basically good and follow them most of the time. I'd love to see data on this, but I feel like it's only the fringe that does not follow them and causes mayhem for the rest of us.",
            "I understand it is a complex issue and I actually have no problem with asylum seekers. I personally believe that we should be letting in people who will come in to this country the legal way and assimilate into our country. This is just my perspective and open to hear the views of others.",
            "I understand why people are worried about the Southern Border situation, but I don't think that has much to do with terrorism. I might be wrong, but I think that more terrorists are coming over the Canadian border.",
            "I understand why some people want  gun control.  It would help insure guns aren't  given to unstable people. But I also believe that as an American I have every right to defend my property, family, and myself with a gun or guns. I worry only criminals would have weapons.",
            "I'm honestly curious about what the other side thinks. I agree that the gangs and the drugs that come over here from Mexico are a problem. At the same time,  I think we already have gangs and drugs over here before Mexico brought them over.",
            "I'm no psychologist, but I don't think that criminals care what the laws are and what they can or can't do. If that is true, they will obtain a gun by whatever means they can, carry it illegally, use it in a crime and possibly use it to rob you.",
            "I'm not an expert on gun policy, but I did write research papers on the topic in college. While doing research, I was persuaded there was a lot misinformation put out by the NRA, which wa led by someone personally enriching himself from the sales of ammunition.",
            "I'm open to hearing other views, but it sure seems like gun control doesn't work. I've heard that the states with the strictest gun control has the highest crime rates and murder rates. I would think that's because only criminal have the guns.",
            "I'm sure others disagree, but I don't think it's our responsibility as a nation to take care of people from other countries who can't get any help from their own government. I think we have enough AMERICANS who need assistance, and we should help them first. I guess I just don't understand why we should be paying for anyone who manages to sneak in to our country.",
            "It's been a long time since I took US history, but I believe this land as far as Texas, New Mexico, Arizona, California, we're all Mexico territory before The United States took it from them. So I guess it would make sense that They're going to come back, maybe because they never left.",
            "Living close to the border has made me think that we need a wall. Our border patrol, who are the real experts, has asked for a wall. I haven't dug into the numbers, but I've heard the wall has already made in a difference in the areas it is in place. I feel we shouldn't ask our border patrol to risk their lives and not give them the tools they ask for.",
            "Others might disagree, but I don't understand the argument that  Mexicans are taking jobs.  If you are unemployed, couldn't find a job anywhere, and a lettuce field in your city that was hiring, would you apply? My sense is that most Americans would say no.",
            "Others might disagree, but I think we need reasonable and uniform NATIONAL gun legislation. I think one reason for the failure of gun control laws in the US is the pathwork of state-to-state differences. I might be wrong, but I think Congress even forbid the government trackingof gun violence deaths.",
            "I'm not an expert, but it seems like more immigration can only hurt me. I'm interesting in hearing the argument for the other side.",
            "I understand the argument that the system needs reform. However, my own view is that many who have immigrated are the epitome of an outstanding citizens that contributes to society and our economy.",
            "I'm open to other ideas, but I wonder if we should require every gun sale to be registered and require gun manufacturers to include trigger locks at no additional charge to the consumer.  It probably won't solve all our problems, but I think that we can take measures to reduce gun deaths without trampling on the 2nd Amendment."
)
posts <- read_csv('./Status Study 12-12-selected/participant-export.csv') %>% 
  bind_rows(read_csv('./Status Study 12-12-selected/export-deleted.csv')) %>%
  filter(participantCode %in% survey_df$participant_code) %>%
  mutate(condition = case_when(
    str_ends(treatmentArm, 'pc') ~ 'pure_control',
    str_ends(treatmentArm, 'treat') ~ 'treat',
    str_detect(treatmentArm, 'control') ~ 'control',
    .default = NA
  )) %>%
  mutate(ih = postOrCommentText %in% ih_posts)

likes <- posts %>%
  filter(participantLiked == 1)

dislikes <- posts %>%
  filter(participantDisliked == 1)


count_tokens <- function(x) {
  x %>%
    tokenize_words() %>%
    sapply(., FUN = length) %>%
    return()
}
content <- posts %>%
  filter(userContent == 1) %>%
  mutate(length = count_tokens(postOrCommentText)) %>%
  mutate(this_is_a_comment = (parentPost != 'N/A'),
         this_is_a_post = (parentPost == 'N/A'))


post_vader_df <- vader::vader_df(content$postOrCommentText) %>%
  select(compound, pos, neg) %>%
  rename(sent_pos = pos,
         sent_neg = neg,
         sent = compound)
content_vader <- content %>%
  bind_cols(post_vader_df) %>%
  select(participantCode, sent_pos, sent_neg, sent)




survey_df <- survey_df %>%
  left_join(likes %>%
              group_by(participantCode) %>%
              mutate(total_likes = n()) %>%
              ungroup() %>%
              group_by(participantCode, ih) %>%
              summarize(ih_likes = n(),
                        total_likes = mean(total_likes),
                        p_likes_ih = ih_likes/total_likes) %>%
              ungroup() %>%
              filter(ih == 1) %>%
              select(-ih), by = c('participant_code' = 'participantCode')) %>%
  left_join(dislikes %>%
              group_by(participantCode) %>%
              mutate(total_dislikes = n()) %>%
              ungroup() %>%
              group_by(participantCode, ih) %>%
              summarize(ih_dislikes = n(),
                        total_dislikes = mean(total_dislikes),
                        p_dislikes_ih = ih_dislikes/total_dislikes) %>%
              ungroup() %>%
              filter(ih == 1) %>%
              select(-ih), by = c('participant_code' = 'participantCode')) %>%
  left_join(content_vader %>%
  group_by(participantCode) %>%
  summarize(sent_pos = mean(sent_pos, na.rm = TRUE),
            sent_neg = mean(sent_neg, na.rm = TRUE),
            sent = mean(sent, na.rm = TRUE)), by = c('participant_code' = 'participantCode')) %>%
  mutate(ih_likes = replace_na(ih_likes, 0),
         p_likes_ih = replace_na(p_likes_ih, 0),
         total_likes = replace_na(total_likes, 0),
         ih_dislikes = replace_na(ih_dislikes, 0),
         p_dislikes_ih = replace_na(p_dislikes_ih, 0),
         total_dislikes = replace_na(total_dislikes, 0))

all_dwell <- posts %>%
  group_by(participantCode) %>%
  summarize(total_dwell_time = sum(dwellTimeInSeconds))

ih_dwell <- posts %>%
  group_by(participantCode, ih) %>%
  summarize(ih_dwell_time = sum(dwellTimeInSeconds)) %>%
  group_by(participantCode) %>%
  mutate(total_dwell_time = sum(ih_dwell_time),
         prop_dwell_time_ih = ih_dwell_time/total_dwell_time) %>%
  filter(ih == 1) %>%
  select(-ih)

survey_df <- survey_df %>%
  left_join(ih_dwell, by = c('participant_code' = 'participantCode'))

```

```{r load third order data, message = FALSE, warning = FALSE, include = FALSE}
third_order <-
  read_csv('./Status Study 12-12-selected/third-order.csv') %>%
  mutate(
    nas = is.na(third_order_A1) + is.na(third_order_A2) + is.na(third_order_B1) + is.na(third_order_B1)
  ) %>%
  filter(nas < 4)

survey_df <- survey_df %>%
  select(-starts_with('third_order')) %>%
  left_join(third_order, by = 'participant_code') %>%
  # replace_na(select(starts_with('third_order_')), 0)
  mutate(across(starts_with('third_order_'), ~replace_na(.x, 0))) %>%
  rowwise() %>%
  mutate(third_order = sum(across(starts_with('third_order'))))
```


# Attrition
```{r load attrition data, message = FALSE, warning = FALSE, include = FALSE}
# 
# total_n <- nrow(intake)
# consent_drop <- intake %>% filter(Consent == 'No, I do NOT consent') %>% nrow()
# jive_drop <-
#   intake %>% filter((platforms_jive == 'A lot') |
#                       (platforms_jive == 'Some')) %>% nrow()
# device_drop <- intake %>%
#   filter((download_apple == 'No, I am NOT') | (download_android == 'No, I am NOT')) %>%
#   nrow()
# 
# download_drop <- intake %>%
#   filter((download_apple == 'No, I am NOT') | (download_android == 'No, I am NOT')) %>%
#   nrow()
# 
# image_drop <- intake %>%
#   filter(screen_image != 3.0) %>%
#   filter(!is.na(screen_image)) %>%
#   nrow()
# 
# age_drop <- intake %>%
#   filter(age < 18) %>%
#   filter(!is.na(age)) %>% 
#   nrow()
# 
# us_drop <- intake %>%
#   filter(state == "I do not reside in the United States") %>%
#   nrow()
# 
# forced_attrit <- consent_drop + jive_drop + device_drop + download_drop + image_drop + age_drop + us_drop
# 
# intake_completes <- intake %>%
#   filter(!is.na(participant_code)) %>%
#   nrow()
# 
# total_attrit_intake <- total_n - intake_completes - forced_attrit
# 
# pretreat_n <- pretreat %>% nrow()
# attrit_intake_pretreat <- intake_completes - pretreat_n
# 
# pretreat_completes <- pretreat %>%
#   filter(!is.na(`Q111_Page Submit`)) %>%
#   nrow()
# 
# posttreat_n <- posttreat %>% nrow()
# 
# attrit_pre_post <- pretreat_completes - posttreat_n
# 
# posttreat_completes <- posttreat %>%
#   filter(Progress >= 93) %>%
#   nrow()


total_n <- nrow(intake_new)
consent_drop <- intake_new %>% filter(Consent == 'No, I do NOT consent') %>% nrow()
jive_drop <-
  intake_new %>% filter((platforms_jive == 'A lot') |
                          (platforms_jive == 'Some')) %>% nrow()
device_drop <- intake_new %>%
  filter((download_apple == 'No, I am NOT') | (download_android == 'No, I am NOT')) %>%
  nrow()

download_drop <- intake_new %>%
  filter((download_apple == 'No, I am NOT') | (download_android == 'No, I am NOT')) %>%
  nrow()

image_drop <- intake_new %>%
  filter(screen_image != 3.0) %>%
  filter(!is.na(screen_image)) %>%
  nrow()

age_drop <- intake_new %>%
  filter(age < 18) %>%
  filter(!is.na(age)) %>% 
  nrow()

us_drop <- intake_new %>%
  filter(state == "I do not reside in the United States") %>%
  nrow()

forced_attrit <- consent_drop + jive_drop + device_drop + download_drop + image_drop + age_drop + us_drop

intake_completes <- intake_new %>%
  filter(!is.na(participant_code)) %>%
  nrow()

total_attrit_intake_new <- total_n - intake_completes - forced_attrit

pretreat_n <- pretreat_new %>% nrow()
attrit_intake_pretreat <- intake_completes - pretreat_n

pretreat_completes <- pretreat_new %>%
  filter(!is.na(`Q111_Page Submit`)) %>%
  nrow()

posttreat_n <- posttreat_new %>% nrow()

attrit_pre_post <- pretreat_completes - posttreat_n

posttreat_completes <- posttreat_new %>%
  filter(Progress >= 93) %>%
  nrow()


```

## Attrition through full study
```{r attrition through study, echo=TRUE, message=FALSE, warning=FALSE, results='asis'}

# sankey diagram should have columns x, node, next_x, next_node
nodes <- tribble(
  ~node, ~stage,
  'Started intake', 1,
  'Finished intake', 2,
  'Did not finish intake', 2,
  'Dropped during download', 3,
  'Started pre-treat' , 3,
  'Finished pre-treat' , 4,
  'Did not finish pre-treat' , 4,
  'Started post-treat' , 5,
  'Lost during newsfeed', 5,
  'Finished post-treat', 6
  ) %>%
  rownames_to_column(var = 'node_index') %>%
  mutate(node_index = as.numeric(node_index) - 1) %>%
  mutate(stage = as.character(stage))

sankey_df <- tribble(
  ~'start', ~'end', ~'n',
  # 'Started intake', NA, total_n,
  'Started intake', 'Finished intake', intake_completes,
  'Started intake', 'Did not finish intake', total_n - intake_completes,
  'Finished intake', 'Dropped during download', attrit_intake_pretreat,
  'Finished intake', 'Started pre-treat', pretreat_n,
  'Started pre-treat', 'Finished pre-treat', pretreat_completes,
  'Started pre-treat', 'Did not finish pre-treat', pretreat_n - pretreat_completes,
  'Finished pre-treat', 'Started post-treat', posttreat_n,
  'Finished pre-treat', 'Lost during newsfeed', pretreat_completes - posttreat_n,
  'Started post-treat', 'Finished post-treat', posttreat_completes,
  # 'Finished post-treat', NA, NA
) %>%
  left_join(nodes, by = c('start' = 'node')) %>%
  rename('start_index' = 'node_index') %>%
  left_join(nodes, by = c('end' = 'node')) %>%
  rename('end_index' = 'node_index'
  )

sankey_plot <- networkD3::sankeyNetwork(
  Links = sankey_df,
  Nodes = nodes,
  Source = "start_index",
  Target = "end_index",
  Value = "n",
  units = "TWh",
  NodeID = 'node',
  NodeGroup = 'stage',
  fontSize = 20,
  nodeWidth = 30,
  sinksRight = FALSE
)


saveNetwork(sankey_plot, "./sn1.html")
# webshot::install_phantomjs()
webshot("sn1.html", "sn1.png", vwidth = 1500, vheight = 500)

```


```{r attrition through intake, echo=TRUE, message=FALSE, warning=FALSE, results='asis'}
n_consented <- intake %>% filter(Consent != 'No, I do NOT consent') %>% nrow()
n_does_not_use_jivehive <- intake %>% 
  filter(platforms_jive != 'A lot') %>%
  filter(platforms_jive != 'Some') %>%
  nrow()
n_lives_in_us <- intake %>%
  filter(state != 'I do not reside in the United States') %>%
  nrow()
n_age_gr_18 <- intake %>%
  filter(age >= 18) %>%
  nrow()
n_android_iphone_user <- intake %>%
  filter(device != 'Something else') %>%
  nrow()
n_will_download_app <- intake %>%
  filter(download_apple != 'No, I am NOT') %>%
  filter(download_android != 'No, I am NOT') %>%
  nrow()
n_passed_3_att_check <- intake %>%
  filter(!is.na(screen_image)) %>%
  filter(screen_image == 3) %>%
  nrow()


intake_drops_nodes <- tribble(
  ~node, ~ stage,
  "Total", 1,
  "Consented", 2,
  "Did not consent", 2,
  "Does not use JiveHive", 3,
  "Uses JiveHive", 3,
  "Lives in US", 4,
  "Lives outside US", 4,
  "Age ≥ 18", 5,
  "Age < 18", 5,
  "Android/iPhone user", 6,
  "Non Android/iPhone user", 6,
  "Download app", 7,
  "Won't download app", 7,
  "Passed `3` attention check", 8,
  "Failed `3` attention check", 8,
  "Unforced attrition", 9,
  "Completed intake", 9
) %>%
  rownames_to_column(var = 'node_index') %>%
  mutate(node_index = as.numeric(node_index) - 1) %>%
  mutate(stage = as.character(stage))
intake_drops_df <- tribble(
  ~'start', ~'end', ~'n',
  'Total', 'Consented', n_consented,
  'Total', 'Did not consent', total_n - n_consented,
  'Consented', 'Does not use JiveHive', n_does_not_use_jivehive,
  'Consented', 'Uses JiveHive', n_consented - n_does_not_use_jivehive,
  'Does not use JiveHive', 'Lives in US', n_lives_in_us,
  'Does not use JiveHive', 'Lives outside US', n_does_not_use_jivehive - n_lives_in_us,
  'Lives in US', 'Age ≥ 18', n_age_gr_18,
  'Lives in US', 'Age < 18', n_lives_in_us - n_age_gr_18,
  'Age ≥ 18', 'Android/iPhone user', n_android_iphone_user,
  'Age ≥ 18', 'Non Android/iPhone user', n_age_gr_18 - n_android_iphone_user,
  'Android/iPhone user', 'Download app', n_will_download_app,
  'Android/iPhone user', 'Won\'t download app', n_android_iphone_user - n_will_download_app,
  'Download app', 'Passed `3` attention check', n_passed_3_att_check,
  'Download app', 'Failed `3` attention check', n_will_download_app - n_passed_3_att_check,
  'Passed `3` attention check', 'Unforced attrition', total_n - intake_completes - forced_attrit,
  'Passed `3` attention check', 'Completed intake', intake_completes
) %>%
  left_join(intake_drops_nodes, by = c('start' = 'node')) %>%
  rename('start_index' = 'node_index') %>%
  left_join(intake_drops_nodes, by = c('end' = 'node')) %>%
  rename('end_index' = 'node_index'
  )


sankey_plot2 <- networkD3::sankeyNetwork(
  Links = intake_drops_df,
  Nodes = intake_drops_nodes,
  Source = "start_index",
  Target = "end_index",
  Value = "n",
  units = "TWh",
  NodeID = 'node',
  NodeGroup = 'stage',
  fontSize = 20,
  nodeWidth = 30,
  sinksRight = FALSE
)


saveNetwork(sankey_plot2, "./sn2.html")
webshot::install_phantomjs()
webshot("sn2.html", "sn2.png", vwidth = 1500, vheight = 500)
```

```{r}
intake_new$finished_intake <- !is.na(intake_new$participant_code)
pretreat_new$finished_pretreat <- !is.na(pretreat_new$`Q111_Page Submit`)
pretreat_new$finished_newsfeed <- (pretreat_new$participant_code %in% posttreat_new$participant_code)
posttreat_new$finished_posttreat <- posttreat_new$Progress >= 93

demog_cols <- c('pid3', 'ideo7', 'race_new', 'device', 'new_educ', 'social_media_high', 'platforms_fb', 'platforms_insta', 'platforms_tiktok', 'platforms_x', 'platforms_truth')
pretreat_cols <- c('pre_ih_binary', 'extremity_pre', 'pre_policy_imm_binary', 'pre_policy_gc_binary', 'political_interest')

pretreat_demogs <- pretreat_new %>%
  left_join(intake_new %>% select(c(demog_cols, 'participant_code', 'Duration (in seconds)', 'state', 'pid7')) %>% rename(`Duration (in seconds)_intake` = `Duration (in seconds)`), by = 'participant_code')
posttreat_pretreat_demogs <- posttreat_new %>%
  left_join(pretreat_demogs %>%
              select(c(demog_cols, pretreat_cols, 'participant_code')),
            by = 'participant_code')

predict_missing <- function(attrit_df, outcome, covariate) {
  df <- attrit_df %>%
    select(!!as.symbol(outcome), !!as.symbol(covariate)) %>%
    drop_na()
  if((df[[covariate]] %>% unique() %>% length()) > 2){
    df <- df %>%
      mutate_at(.funs = as.factor, .vars = c(covariate))
    
    ref <- levels(df[[covariate]])[1]
  } else {
    ref <- NA
  }

  glm_result <-
    glm(
      formula = paste0(outcome, '~', covariate),
      family = 'binomial',
      data = df
    )
  
  return_df <- glm_result %>% 
    summary() %>% 
    .$coefficients %>% 
    as.data.frame() %>% 
    mutate(outcome = outcome) %>% 
    mutate(reference = ref) %>% 
    rownames_to_column()
  
  return(return_df)
}
attrit_regs <- predict_missing(intake_new, 'finished_intake', 'pid3') %>%
bind_rows(predict_missing(intake_new, 'finished_intake', 'ideo7')) %>%
bind_rows(predict_missing(intake_new, 'finished_intake', 'race_new')) %>%
bind_rows(predict_missing(intake_new, 'finished_intake', 'device')) %>%
bind_rows(predict_missing(intake_new, 'finished_intake', 'new_educ')) %>%
bind_rows(predict_missing(intake_new, 'finished_intake', 'social_media_high')) %>%
bind_rows(predict_missing(intake_new, 'finished_intake', 'platforms_fb')) %>%
bind_rows(predict_missing(intake_new, 'finished_intake', 'platforms_insta')) %>%
bind_rows(predict_missing(intake_new, 'finished_intake', 'platforms_tiktok')) %>%
bind_rows(predict_missing(intake_new, 'finished_intake', 'platforms_x')) %>%
bind_rows(predict_missing(intake_new, 'finished_intake', 'platforms_truth')) %>%
bind_rows(predict_missing(pretreat_demogs, 'finished_pretreat', 'pid3')) %>%
bind_rows(predict_missing(pretreat_demogs, 'finished_pretreat', 'ideo7')) %>%
bind_rows(predict_missing(pretreat_demogs, 'finished_pretreat', 'race_new')) %>%
bind_rows(predict_missing(pretreat_demogs, 'finished_pretreat', 'device')) %>%
bind_rows(predict_missing(pretreat_demogs, 'finished_pretreat', 'new_educ')) %>%
bind_rows(predict_missing(pretreat_demogs, 'finished_pretreat', 'social_media_high')) %>%
bind_rows(predict_missing(pretreat_demogs, 'finished_pretreat', 'platforms_fb')) %>%
bind_rows(predict_missing(pretreat_demogs, 'finished_pretreat', 'platforms_insta')) %>%
bind_rows(predict_missing(pretreat_demogs, 'finished_pretreat', 'platforms_tiktok')) %>%
bind_rows(predict_missing(pretreat_demogs, 'finished_pretreat', 'platforms_x')) %>%
bind_rows(predict_missing(pretreat_demogs, 'finished_pretreat', 'platforms_truth')) %>%
bind_rows(predict_missing(pretreat_demogs, 'finished_newsfeed', 'pid3')) %>%
bind_rows(predict_missing(pretreat_demogs, 'finished_newsfeed', 'ideo7')) %>%
bind_rows(predict_missing(pretreat_demogs, 'finished_newsfeed', 'race_new')) %>%
bind_rows(predict_missing(pretreat_demogs, 'finished_newsfeed', 'device')) %>%
bind_rows(predict_missing(pretreat_demogs, 'finished_newsfeed', 'new_educ')) %>%
bind_rows(predict_missing(pretreat_demogs, 'finished_newsfeed', 'social_media_high')) %>%
bind_rows(predict_missing(pretreat_demogs, 'finished_newsfeed', 'platforms_fb')) %>%
bind_rows(predict_missing(pretreat_demogs, 'finished_newsfeed', 'platforms_insta')) %>%
bind_rows(predict_missing(pretreat_demogs, 'finished_newsfeed', 'platforms_tiktok')) %>%
bind_rows(predict_missing(pretreat_demogs, 'finished_newsfeed', 'platforms_x')) %>%
bind_rows(predict_missing(pretreat_demogs, 'finished_newsfeed', 'platforms_truth')) %>%
mutate(Estimate = round(Estimate, 2)) %>%
mutate(stars = case_when(`Pr(>|z|)` <= 0.05 ~ '*',
                         `Pr(>|z|)` <= 0.01 ~ '**',
                         `Pr(>|z|)` <= 0.001 ~ '***',
                         .default = ' ')) %>%
  filter(rowname != '(Intercept)') %>%
  # filter(stars != ' ') %>%
  # filter(!is.na(stars)) %>%
  mutate(Estimate = paste0(Estimate, stars)) %>%
  pivot_wider(id_cols = c(rowname, reference), names_from = outcome, values_from = Estimate) %>%
  filter(str_ends(finished_intake, ' ') + str_ends(finished_pretreat, ' ') + str_ends(finished_newsfeed, ' ') < 3)

# i <- 'platforms_tiktok'
# intake_new %>%
#   filter(!is.na(!!as.symbol(i))) %>%
#   group_by(finished_intake, !!as.symbol(i)) %>%
#   count()

attrit_regs %>%
  pander::pander(caption = 'First column displays covariate/level, second column displays the reference level, and the following columns represent the drop point of investigation. *=p<0.05, **=p<0.01, ***=p<0.001.')

```

```{r are treated conservatives more likely to drop during the newsfeed}
pretreat_demogs %>%
  mutate(condition = case_when(
    str_ends(treatment_arm, 'pc') ~ 'pure_control',
    str_ends(treatment_arm, 'treat') ~ 'treat',
    str_detect(treatment_arm, 'control') ~ 'control',
    .default = NA)
  ) %>%
  mutate(ideo7 = as.factor(ideo7)) %>%
  filter(!is.na(ideo7)) %>%
  glm(formula = "finished_newsfeed ~ ideo7 * condition", family = 'binomial') %>%
  summary() %>%
  pander::pander(caption = 'No significant difference between newsfeed dropout based on political party')

```

```{r are treated respondents more likely to drop during the newsfeed (written by Chris)}
pretreat_demogs %>%
  mutate(condition = case_when(
    str_ends(treatment_arm, 'pc') ~ 'pure_control',
    str_ends(treatment_arm, 'treat') ~ 'treat',
    str_detect(treatment_arm, 'control') ~ 'control',
    .default = NA)
  ) %>%
  mutate(ideo7 = as.factor(ideo7)) %>%
  filter(!is.na(ideo7)) %>%
  glm(formula = "finished_newsfeed ~ condition", family = 'binomial') %>%
  summary() %>%
  pander::pander(caption = 'No significant difference between newsfeed dropout based on treatment condition')

```

```{r}

crash_times <- tribble(
  ~start, ~end,
  '12/12/2023 11:25', '12/12/2023 11:27',
  '12/12/2023 11:31', '12/12/2023 11:33',
  '12/12/2023 11:36', '12/12/2023 11:38',
  '12/12/2023 11:42', '12/12/2023 11:44',
  '12/13/2023 14:50', '12/13/2023 14:50',
  '12/13/2023 14:56', '12/13/2023 14:58',
  '12/13/2023 15:14', '12/13/2023 15:16',
  '12/13/2023 15:17', '12/13/2023 15:19',
  '12/13/2023 15:22', '12/13/2023 15:24',
  '12/13/2023 15:24', '12/13/2023 15:26'
) %>%
  mutate_all(.funs = ~lubridate::as_datetime(., format = '%m/%d/%Y %H:%M'))



check_crash <- function(start_time, end_time) {
  survivor <- TRUE
  for (i in 1:nrow(crash_times)) {
    if((start_time <= crash_times$start[i]) & (end_time >= crash_times$end[i]))
      return(FALSE)
  }
  return(survivor)
}


survivors <- c()
end_time <- c()
survey_df <- survey_df %>%
  mutate(StartDate = lubridate::as_datetime(StartDate, format = '%m/%d/%Y %H:%M')) %>%
  mutate(end_time = case_when(
    !is.na(EndDate_post) ~ lubridate::as_datetime(EndDate_post, format = '%m/%d/%Y %H:%M'),
    !is.na(EndDate_pre) ~ lubridate::as_datetime(EndDate_pre, format = '%m/%d/%Y %H:%M'),
    !is.na(EndDate) ~ lubridate::as_datetime(EndDate, format = '%m/%d/%Y %H:%M'),
    .default = StartDate + lubridate::dseconds(`Duration (in seconds)`)
  )) %>%
  mutate(crash_survivor = check_crash(StartDate, end_time))
```

The crash affected `r nrow(survey_df) - sum(survey_df$crash_survivor)` participants.


# Analytical sample definition
### Survey Completion Time
```{r survey completion time, message=FALSE, warning=FALSE}
survey_df$pretreatment_intake_time <- survey_df$`Duration (in seconds)` + survey_df$`Duration (in seconds)_pre`
survey_df$speeder <- survey_df$pretreatment_intake_time <= median(survey_df$pretreatment_intake_time)/4 %>%
  replace_na(FALSE)
survey_df %>%
  ggplot() +
  geom_histogram(aes(x = pretreatment_intake_time), alpha = 0.5) +
  scale_x_log10() +
  geom_vline( aes(xintercept = median(pretreatment_intake_time)/2, linetype = 'Median/2')) +
  geom_vline( aes(xintercept = median(pretreatment_intake_time)/4, linetype = 'Median/4')) +
  labs(
    x = 'Pre-treatment and intake completion time (in sec)',
    y = 'Count',
    linetype = 'Threshold',
    title = 'Survey Completion Time',
    subtitle = paste0('#Speeders (Time <= Median/4): ', sum(survey_df$speeder))
  )

sum(survey_df$pretreatment_intake_time <= median(survey_df$pretreatment_intake_time)/2)
```

## Zip code/state matches
```{r zip code/state matches, message = FALSE, warning = FALSE}
# survey_df$state_from_zip <-
survey_df <- survey_df %>%
  mutate(zipcode = case_when(
    nchar(zip) == 4 ~ paste0('0', zip),
    .default = zip
  ))


survey_df <- zip_code_db %>%
  select(zipcode, state) %>%
  rename(zip_state = state) %>%
  right_join(survey_df, by = c('zipcode')) %>%
  mutate(
    zip_state =
      case_when(
        zipcode == '77407' ~ "TX",
        zipcode == '85756' ~ "AZ",
        zipcode == '49519' ~ "MI",
        zipcode == "34638" ~ "FL",
        zipcode == "25405" ~ "WV",
        zipcode == "10065" ~ "NY",
        zipcode == "89183" ~ "NV",
        zipcode == "89178" ~ "NV",
        zipcode == "85143" ~ "AZ",
        zipcode == "85140" ~ "AZ",
        zipcode == "32163" ~ "FL",
        zipcode == "85119" ~ "AZ",
        zipcode == "29486" ~ "SC",
        zipcode == "85142" ~ "AZ",
        zipcode == "60169" ~ "IL",
        zipcode == "98391" ~ "WA",
        zipcode == "80923" ~ "CO",
        # https://researchmaniacs.com/ZipCodes/4/Where-is-Zip-Code-46907.html
        zipcode == "46907" ~ "IN",
        zipcode == "10486" ~ "NY",
        zipcode == "91760" ~ "CA",
        zipcode == "00000" ~ NA,
        zipcode == "46343" ~ "IN",
        zipcode == "90289" ~ "CA",
        zipcode == "90268" ~ "CA",
        .default = zip_state)
  ) %>%
  mutate(state_full = get_state_names(zip_state))

survey_df <- survey_df %>%
  mutate(pass_zip_check = (survey_df$state_full == survey_df$state)) %>%
  mutate(pass_zip_check = replace_na(pass_zip_check, replace = FALSE))

pretreat_demogs <- zip_code_db %>%
  select(zipcode, state) %>%
  rename(zip_state = state) %>%
  right_join(pretreat_demogs, by = c('zipcode' = 'zip')) %>%
  mutate(
    zip_state =
      case_when(
        zipcode == '77407' ~ "TX",
        zipcode == '85756' ~ "AZ",
        zipcode == '49519' ~ "MI",
        zipcode == "34638" ~ "FL",
        zipcode == "25405" ~ "WV",
        zipcode == "10065" ~ "NY",
        zipcode == "89183" ~ "NV",
        zipcode == "89178" ~ "NV",
        zipcode == "85143" ~ "AZ",
        zipcode == "85140" ~ "AZ",
        zipcode == "32163" ~ "FL",
        zipcode == "85119" ~ "AZ",
        zipcode == "29486" ~ "SC",
        zipcode == "85142" ~ "AZ",
        zipcode == "60169" ~ "IL",
        zipcode == "98391" ~ "WA",
        zipcode == "80923" ~ "CO",
        # https://researchmaniacs.com/ZipCodes/4/Where-is-Zip-Code-46907.html
        zipcode == "46907" ~ "IN",
        zipcode == "10486" ~ "NY",
        zipcode == "91760" ~ "CA",
        zipcode == "00000" ~ NA,
        zipcode == "46343" ~ "IN",
        zipcode == "90289" ~ "CA",
        zipcode == "90268" ~ "CA",
        .default = zip_state)
  ) %>%
  mutate(state_full = get_state_names(zip_state)) %>%
  mutate(pass_zip_check = (state_full == state)) %>%
  mutate(pass_zip_check = replace_na(pass_zip_check, replace = FALSE)) %>%
  mutate(speeder = (`Duration (in seconds)_intake` + `Duration (in seconds)`) <= median(survey_df$pretreatment_intake_time)/4)

glm(
  finished_newsfeed ~ factor(pid7) + pass_zip_check + speeder,
  family = 'binomial',
  data = pretreat_demogs
)
```

### Bonus word check
```{r bonus check, echo=FALSE, message=FALSE, warning=FALSE}
survey_df$correct_bonus <- survey_df$password %>%
  str_to_lower() %>%
  str_detect('win') %>%
  replace_na(FALSE)
```

### Made 1+ post and 1+ comment
```{r at least one post and comment, echo=FALSE, message=FALSE, warning=FALSE}
survey_df <- survey_df %>%
  right_join(content %>%
  group_by(participantCode) %>%
  summarize(n_posts = sum(this_is_a_post),
            n_comments = sum(this_is_a_comment)), by = c('participant_code' = 'participantCode')) %>%
  mutate(participant_commented = (n_comments >= 1) & !is.na(n_comments),
         participant_posted = (n_posts >= 1) & !is.na(n_posts))
```


```{r venn diagram, message = FALSE, warning = FALSE, echo = FALSE}

ggplot(survey_df) +
  geom_venn(aes(A = !speeder, B = pass_zip_check, C = correct_bonus, D = (mc_correct == 1), E = participant_commented, G = participant_posted), show_percentage = FALSE,
            set_names = c('Did not speed', 'Zip code state = Reported state', 'Correct bonus word', 'Correct manip check', 'Commented', 'Posted'),
            fill_color = c('#3b528b', '#21918c', '#5ec962', '#1ff340', '#6b528b', '#9b528b')) +
  scale_fill_viridis_b() +
  theme_classic() +
  theme(axis.text.x=element_blank(),
      axis.ticks.x=element_blank(),
      axis.text.y=element_blank(),
      axis.ticks.y=element_blank(),
      axis.line.x = element_blank(),
      axis.line.y = element_blank())
```

```{r participant check, message = FALSE, warning = FALSE, echo = FALSE}
survey_df %>%
  group_by(!speeder, pass_zip_check, correct_bonus, (mc_correct == 1), participant_commented, participant_posted) %>%
  count() %>%
  rename(`Did not speed` = `!speeder`,
         `Zip code state = Reported state` = pass_zip_check,
         `Correct bonus word` = correct_bonus,
         `Pass manip check` = `(mc_correct == 1)`,
         `Commented` = participant_commented,
         `Posted` = participant_posted) %>%
  arrange(-n) %>%
  pander::pander()
```

```{r extreme cons attrition check, message = FALSE, warning = FALSE, echo = FALSE}

pretreat_demogs %>%
    select(finished_newsfeed, ideo7, pass_zip_check, speeder) %>%
    drop_na() %>%
  mutate_at(.funs = as.factor, .vars = c('ideo7')) %>%
  glm(formula = 'finished_newsfeed ~ ideo7 + pass_zip_check + speeder', family = 'binomial', data = .) %>%
  summary()
```


## Demographic/Balance checks
### Age
```{r demog and balance checks, echo=FALSE, message=FALSE, warning=FALSE}

demogs_plot <- function(col, factor_list = NULL, title = NA, balance_all_groups = TRUE) {
  if(!is.null(factor_list)) {
    survey_df <- survey_df %>%
      mutate_at(.vars = c(col), .funs = function(x) factor(x, levels = factor_list))
  }
  if(!balance_all_groups) {
    survey_df <- survey_df %>%
      filter(condition != 'pure_control')
  }
  if(col %in% c('age', 'therm_diff_pre', 'pre_ih')) {
  p <- ggplot(survey_df) +
      geom_histogram(aes_string(x = col, fill = 'condition'), position = 'identity', alpha = 0.5, stat = 'count')
    if(balance_all_groups) {
      p_value <- min(ks.test(survey_df[survey_df$condition == 'treat', col],
                           survey_df[survey_df$condition == 'control', col])$p.value,
                   ks.test(survey_df[survey_df$condition == 'treat', col],
                           survey_df[survey_df$condition == 'pure_control', col])$p.value,
                   ks.test(survey_df[survey_df$condition == 'pure_control', col],
                           survey_df[survey_df$condition == 'control', col])$p.value
                   )
    } else {
      p_value <-  ks.test(survey_df[survey_df$condition == 'treat', col],
                           survey_df[survey_df$condition == 'control', col])$p.value
    }
  }
  else {
    p <- ggplot(survey_df) +
      geom_histogram(aes_string(x = col, fill = 'condition'), position = 'dodge2', stat = 'count')
    p_value <- survey_df %>%
      group_by(condition, (!!as.symbol(col))) %>%
      count() %>%
      pivot_wider(id_cols = 'condition', names_from = col, values_from = 'n') %>%
      ungroup() %>%
      column_to_rownames('condition') %>%
      as.matrix() %>%
      chisq.test() %>%
      .$p.value
  }
  p <- p +
    theme(legend.position = 'bottom',
          axis.text.x = element_text(angle = 45, hjust = 1)) +
    labs(title = paste0('Histogram of `', title, '`'),
         subtitle = paste0('#Missing values: ', is.na(survey_df[col]) %>% sum()),
         caption = paste0('Min p-value from KS/Chi^2 test between groups: ', round(p_value, 4)),
         x = title)
  return(p)
}

demogs_plot('race_new', title = 'Race')
demogs_plot('age', title = 'Age')

demogs_plot('pid3', c('Democrat', 'Independent', 'Republican', 'Other'), title = 'Political Identity')
demogs_plot('pid7', c('Strong Democrat',
                       'Weak Democrat',
                       'Lean Democrat',
                       'True Independent/Other',
                       'Lean Republican',
                       'Weak Republican',
                       'Strong Republican'), title = 'Political Identity')
demogs_plot('ideo7',
            c('Extremely liberal', 'Liberal', 'Somewhat liberal', 'Moderate or middle of the road', 'Somewhat conservative', 'Conservative', 'Extremely conservative'),
            'Ideology')

demogs_plot('new_educ', c('Less than high school',
                          'High school graduate or equivalent (GED)',
                          'Some college but no degree',
                          'Associate degree in college',
                          'Bachelor’s degree',
                          'Post-graduate degree'),
            'Education')

demogs_plot('race_new', title = 'Race', balance_all_groups = FALSE)
demogs_plot('age', title = 'Age', balance_all_groups = FALSE)
demogs_plot('pid3', c('Democrat', 'Independent', 'Republican', 'Other'), title = 'Political Identity', balance_all_groups = FALSE)
demogs_plot('pid7', c('Strong Democrat',
                       'Weak Democrat',
                       'Lean Democrat',
                       'True Independent/Other',
                       'Lean Republican',
                       'Weak Republican',
                       'Strong Republican'), title = 'Political Identity', balance_all_groups = FALSE)
demogs_plot('ideo7',
            c('Extremely liberal', 'Liberal', 'Somewhat liberal', 'Moderate or middle of the road', 'Somewhat conservative', 'Conservative', 'Extremely conservative'),
            'Ideology', balance_all_groups = FALSE)

demogs_plot('new_educ', c('Less than high school',
                          'High school graduate or equivalent (GED)',
                          'Some college but no degree',
                          'Associate degree in college',
                          'Bachelor’s degree',
                          'Post-graduate degree'),
            'Education', balance_all_groups = FALSE)
demogs_plot('therm_diff_pre', NULL, 'Pre-treatment affective polarization', balance_all_groups = FALSE)
demogs_plot('pre_ih', NULL, 'Pre-treatment intellectual humility', balance_all_groups = FALSE)
demogs_plot('pre_policy_gc', NULL, 'Pre-treatment gun control views', balance_all_groups = FALSE)
demogs_plot('pre_policy_imm', NULL, 'Pre-treatment immigration views', balance_all_groups = FALSE)
```


<!-- # Attrition Checks -->
<!-- ```{r attrition, echo=FALSE, include=FALSE, warnings=FALSE, error=FALSE} -->
<!-- intake_w_nas <- read_csv('./Status Study 12-12-selected/intake.csv') %>% -->
<!--   mutate(participant_code = participant_code_replacements(PROLIFIC_PID, participant_code)) %>% -->
<!--   mutate(participant_code = str_to_lower(participant_code)) -->
<!-- pretreat_w_nas <- read_csv('./Status Study 12-12-selected/pre.csv') -->
<!-- posttreat_w_nas <- read_csv('./Status Study 12-12-selected/post.csv') -->



<!-- intake_w_nas %>% -->
<!--   mutate(consent_drop = (Consent == 'No, I do NOT consent'), -->
<!--          jive_drop = (platforms_jive == 'A lot') | (platforms_jive == 'Some'), -->
<!--          device_drop = device == 'Something else', -->
<!--          download_drop = (download_apple == 'No, I am NOT') | (download_android == 'No, I am NOT'), -->
<!--          image_drop = (screen_image != 3), -->
<!--          age_drop = (age < 18), -->
<!--          us_drop = (state == 'I do not reside in the United States'), -->
<!--          intake_complete = !is.na(participant_code)) %>% -->
<!--   group_by(across(ends_with('_drop'))) %>% -->
<!--   count() %>% -->
<!--   ungroup() %>% -->
<!--   pivot_longer(cols = -n) %>% -->
<!--   filter(!is.na(value)) -->

<!-- ``` -->



# Main Hypothesis Tests
```{r main ttest code, message=FALSE, warning=FALSE}
main_hypothesis_test <- function(df,
                                 outcome,
                                 main_condition = 'treat',
                                 contrast_condition = 'control',
                                 display_plot = FALSE,
                                 title = '',
                                 return_object = FALSE) {
  # isolate data for main group and contrast group
  outcome_main_group <- df %>%
    filter(condition == main_condition) %>%
    .[outcome] %>%
    drop_na() %>%
    pull(.)

  outcome_contrast_group <- df %>%
    filter(condition == contrast_condition) %>%
    .[outcome] %>%
    drop_na() %>%
    pull(.)

  # run t test comparing these two groups
  ttest_results <- t.test(
    x = outcome_main_group,
    y = outcome_contrast_group,
    alternative = 'two.sided',
    var.equal = FALSE
  )
  # ttest_estimate <- ttest_results$
  ttest_pvalue <- ttest_results$p.value
  ttest_cohens_d <- effsize::cohen.d(outcome_main_group,
                                     outcome_contrast_group)$estimate

  # make ttest plot
  n_stars <- ''
  if(ttest_pvalue < 0.05) { n_stars <- '*'}
  else if(ttest_pvalue < 0.01) { n_stars <- '**'}
  else if(ttest_pvalue < 0.001) { n_stars <- '***' }
  p <- ggplot() +
    geom_bar(aes(x = outcome_main_group, y = ..prop.., fill = main_condition), alpha = 0.5, position = 'identity') +
    geom_bar(aes(x = outcome_contrast_group, y = ..prop.., fill = contrast_condition), alpha = 0.5, position = 'identity') +
    geom_density(aes(x = outcome_main_group, fill = main_condition), alpha = 0.5, position = 'identity') +
    geom_density(aes(x = outcome_contrast_group, fill = contrast_condition), alpha = 0.5, position = 'identity') +
    geom_vline(aes(xintercept = mean(outcome_main_group), linetype = main_condition), linewidth = 1) +
    geom_vline(aes(xintercept = mean(outcome_contrast_group), linetype = contrast_condition), linewidth = 1) +
    labs(x = outcome,
         y = 'density',
         title = paste0(title, ': ', outcome, n_stars),
         subtitle = paste0('(p=', round(ttest_pvalue, 3), ', D=', round(ttest_cohens_d, 3), ')'),
         fill = 'Contrast groups',
         linetype = 'Contrast groups'
         )

  if(ttest_pvalue < 0.05) {
    p <- p +
      theme(plot.title = element_text(face = 'bold'),
            plot.subtitle = element_text(face = 'bold'))
  }
return_list <- list('contrast' = paste(main_condition, 'vs', contrast_condition),
                    'ttest' = ttest_results,
                    'p.value' = ttest_pvalue,
                    'cohen.d' = ttest_cohens_d,
                    'plot' = p)
  # if you should display the plot, make the plot and display it
  if(display_plot) print(p)
  if(return_object) return(return_list)
}

subgroup_hypothesis_test <- function(df,
                                 outcome,
                                 subgroup_col,
                                 subgroup_rhs,
                                 main_condition = 'treat',
                                 contrast_condition = 'control',
                                 display_plot = FALSE,
                                 title = '',
                                 return_object = FALSE) {
  result <- main_hypothesis_test(
    df %>% filter(.data[[subgroup_col]] == subgroup_rhs),
    outcome,
    main_condition,
    contrast_condition,
    display_plot,
    title = paste0(title, subgroup_col, '=', subgroup_rhs),
    return_object = TRUE
  )
  if (return_object) return(result)
}

multiple_subgroups_htest <- function(df,
                                 outcome,
                                 subgroup_cols,
                                 subgroup_rhss,
                                 main_condition = 'treat',
                                 contrast_condition = 'control',
                                 display_plot = FALSE,
                                 title = '',
                                 return_object = FALSE)
  {
  row_names <- paste0(subgroup_cols, '=', subgroup_rhss)
  subgroup_results <- data.frame('contrast' = rep(NA, length(row_names)),
                                 'ttest' = rep(NA, length(row_names)),
                                 'p.value' = rep(NA, length(row_names)),
                                 'cohen.d' = rep(NA, length(row_names)),
                                 'plot' = rep(NA, length(row_names)),
                                 row.names = paste0(subgroup_cols, '=', subgroup_rhss))
  for(index in 1:length(subgroup_cols)) {
    sg_result <- subgroup_hypothesis_test(survey_df,
                           outcome = outcome,
                           subgroup_col = subgroup_cols[index],
                           subgroup_rhs = subgroup_rhss[index],
                           display_plot = display_plot,
                           return_object = TRUE)
    subgroup_results[paste0(subgroup_cols[index], '=', subgroup_rhss[index]), ] <- sg_result
  }
  subgroup_results$outcome <- outcome
  subgroup_results$subgroup <- rownames(subgroup_results)
  rownames(subgroup_results) <- NULL
  if(return_object) return(subgroup_results)
}
```



## Hypothesis 1A: experience less negative emotions
```{r h1a, echo=FALSE, warning=FALSE}
main_hypothesis_test(survey_df, 'panas_neg', display_plot = TRUE, title = 'All participants', return_object = FALSE)
```

## Hypothesis 1B: experience more positive emotions
```{r h1b, echo=FALSE, warning=FALSE}
main_hypothesis_test(survey_df, 'panas_pos', display_plot = TRUE, title = 'All participants', return_object = FALSE)
```

## Hypothesis 1C: experience more positive and less negative emotions
```{r h1c, echo=FALSE, warning=FALSE}
main_hypothesis_test(survey_df, 'panas', display_plot = TRUE, title = 'All participants', return_object = FALSE)
```

## Hypothesis 2: report greater increases in their intellectual humility
```{r h2, echo=FALSE, warning=FALSE}
main_hypothesis_test(survey_df, 'delta_ih', display_plot = TRUE, title = 'All participants', return_object = FALSE)
```

## Hypothesis 3: produce more intellectually humble content

## Hypothesis 4: engage more with intellectually humble content


## Hypothesis 5: experience a greater reduction in their affective polarization
```{r h5, echo=FALSE, warning=FALSE}
main_hypothesis_test(survey_df, 'affective_polarization', display_plot = TRUE, title = 'All participants', return_object = FALSE)
```

## Hypothesis 6: moderate their issue positions to a greater degree
```{r h6, echo=FALSE, warning=FALSE}
main_hypothesis_test(survey_df, 'extremity_post_less_pre', display_plot = TRUE, title = 'All participants', return_object = FALSE)
```


## Subgroup Analyses
```{r subgroup, echo=TRUE, warning=FALSE}

subgroup_cols <- c('pre_ih_binary',
                   'pre_ih_binary',
                   'social_media_high',
                   'social_media_high',
                   'pid3',
                   'pid3')
subgroup_rhss <- list(TRUE, FALSE, 1, 0, 'Democrat', 'Republican')

subgroup <- lapply(X = list('panas_neg', 'panas_pos', 'panas', 'delta_ih', 'affective_polarization', 'extremity_post_less_pre'),
       function(x) multiple_subgroups_htest(
  df = survey_df,
  outcome = x,
  subgroup_cols = subgroup_cols,
  subgroup_rhss = subgroup_rhss,
  main_condition = 'treat',
  contrast_condition = 'control',
  display_plot = FALSE,
  title = '',
  return_object = TRUE
)) %>%
  bind_rows()

subgroup %>%
  filter(p.value <= 0.05) %>%
  select(p.value, cohen.d, outcome, subgroup) %>%
  mutate(stars = case_when(
    p.value <= 0.001 ~ '***',
    p.value <= 0.01 ~ '**',
    p.value <= 0.05 ~ '*'
  )) %>%
  mutate(cohen.d = paste0(round(cohen.d, 3), stars)) %>%
  pivot_wider(id_cols = 'subgroup', names_from = 'outcome', values_from = 'cohen.d') %>%
  column_to_rownames('subgroup') %>%
  pander::pander(caption = 'Rows represent subgroups, columns represent outcome, and entries represent effect size. p<0.05*, p<0.01**, p<0.001***')
```



## Other Questions
### How do descriptions of the platform differ between treated and control users?
```{r description of platform, echo=TRUE, warning=FALSE}
main_hypothesis_test(survey_df, 'engaging', display_plot = TRUE, title = 'All participants, platform description')
main_hypothesis_test(survey_df, 'toxic', display_plot = TRUE, title = 'All participants, platform description')
main_hypothesis_test(survey_df, 'exhausting', display_plot = TRUE, title = 'All participants, platform description')
```

### How do descriptions of other users differ between treated and control users?
```{r description of users, echo=TRUE, warning=FALSE}
main_hypothesis_test(survey_df, 'polite', display_plot = TRUE, title = 'All participants, user description')
main_hypothesis_test(survey_df, 'aggressive', display_plot = TRUE, title = 'All participants, user description')
main_hypothesis_test(survey_df, 'tolerant', display_plot = TRUE, title = 'All participants, user description')
```

### How does treatment affect comfort in sharing ideas?
```{r comfort sharing, echo = TRUE, warning = FALSE}
main_hypothesis_test(survey_df, 'comfort', display_plot = TRUE, title = 'All participants, user description')
```

### Estimation of bots
```{r bot estimation, echo = TRUE, warning = FALSE}
survey_df %>% 
  group_by(bots) %>% 
  count() %>%
  ungroup() %>%
  mutate(prop = round(n/sum(n), 3))
```


### How does treatment affect engagement with the platform?
```{r ih likes vs total ilkes, echo = TRUE, warning = FALSE}

ggplot(survey_df) +
  geom_histogram(aes(x = p_likes_ih, y = ..density.., fill = condition), position = 'identity', alpha = 0.4) +
  geom_density(aes(x = p_likes_ih, fill = condition), position = 'identity', alpha = 0.4) +
  labs(x = 'Proportion of liked posts that were IH',
       title = 'Proportion of liked posts that were IH by condition')
```


```{r ih dislikes vs total dislikes, echo = TRUE, warning = FALSE}

ggplot(survey_df) +
  geom_histogram(aes(x = p_likes_ih, y = ..density.., fill = condition), position = 'identity', alpha = 0.4) +
  geom_density(aes(x = p_likes_ih, fill = condition), position = 'identity', alpha = 0.4) +
  labs(x = 'Proportion of liked posts that were IH',
       title = 'Proportion of liked posts that were IH by condition')

ggplot(survey_df) +
  geom_histogram(aes(x = p_dislikes_ih, y = ..density.., fill = condition), position = 'identity', alpha = 0.4) +
  geom_density(aes(x = p_dislikes_ih, fill = condition), position = 'identity', alpha = 0.4) +
  labs(x = 'Proportion of disliked posts that were IH',
       title = 'Proportion of disliked posts that were IH by condition')


```

### How does dwell time relate to outcome measures?
```{r dwell time, message=FALSE, warning=FALSE}

ggplot(survey_df) +
  geom_histogram(aes(x = prop_dwell_time_ih, y = ..density.., fill = condition), alpha = 0.5, position =  'identity') +
  geom_density(aes(x = prop_dwell_time_ih, fill = condition), alpha = 0.5, position = 'identity') +
  labs(x = 'Proportion of time spent on IH posts')


ggplot(survey_df) +
  geom_point(aes(x = ih_dwell_time, y = panas, color = condition), alpha = 0.5) +
  geom_smooth(aes(x = ih_dwell_time, y = panas, color = condition), alpha = 0.5) +
  geom_smooth(aes(x = ih_dwell_time, y = panas), alpha = 1, color = 'black') +
  labs(x = 'Dwell time on IH posts (Seconds)',
       y = 'Emotional Experience (PANAS)')



survey_df %>%
  select(
    ih_dwell_time,
    panas,
    # third_order,
    delta_ih,
    # future_use_n,
    engaging,
    toxic,
    exhausting,
    platforms,
    polite,
    aggressive,
    tolerant,
    users,
    users_b,
    comfort
  ) %>%
  pivot_longer(cols = -ih_dwell_time) %>%
  group_by(name) %>%
  summarize(pearson_p = cor.test(ih_dwell_time, value, method = 'pearson')$p.value %>% round(., 3),
            pearson = cor.test(ih_dwell_time, value, method = 'pearson')$estimate  %>% round(., 3),
            spearman_p = cor.test(ih_dwell_time, value, method = 'spearman')$p.value %>% round(., 3),
            spearman = cor.test(ih_dwell_time, value, method = 'spearman')$estimate  %>% round(., 3)) %>% pander::pander()
```



# Heterogeneous treatment effects using BART: Installation issues. Can't do `BCF` now

- Currently handle missing values by dropping all observations with `NA`s




```{r echo=TRUE, message=FALSE, warning=FALSE}
library(dbarts)
library(fastDummies)
library(janitor)

# outcome_cols <- c('panas', 'panas_pos', 'panas_neg', 'delta_ih', 'affective_polarization', 'extremity_post_less_pre', 'third_order')
outcome_cols <- c('panas', 'panas_pos', 'panas_neg', 'delta_ih', 'extremity_post_less_pre', 'third_order')

cate_survey_df_original_names <- survey_df %>%
  # select(all_of(c(demog_cols, pretreat_cols, outcome_cols, 'condition', 'pre_ih', 'age', 'pid7', 'therm_diff_pre', 'pid_extremity'))) %>%
  select(all_of(c(demog_cols, pretreat_cols, outcome_cols, 'condition', 'pre_ih', 'age', 'pid7', 'pid_extremity', 'bots'))) %>%
    drop_na()

cate_survey_df <- cate_survey_df_original_names %>%
  fastDummies::dummy_columns(select_columns = c(demog_cols, pretreat_cols), 
                             remove_selected_columns = TRUE) %>%
  janitor::clean_names()
  


tlearner_bart <- function(x.train_treat, y.train_treat, x.train_control, y.train_control, x.test) {
  bart_treat <- dbarts::bart(x.train = x.train_treat,
                             y.train = y.train_treat,
                             keeptrees = TRUE,
                             verbose = FALSE)
  bart_control <- dbarts::bart(x.train = x.train_control,
                               y.train = y.train_control,
                               keeptrees = TRUE,
                               verbose = FALSE)
  y1 <- predict(bart_treat, x.test)
  y0 <- predict(bart_control, x.test)
  return_obj <- list('bart_treat' = bart_treat,
                     'bart_control' = bart_control,
                     cate = y1 - y0)
  return(colMeans(y1) - colMeans(y0))
}

cate_estimates <- sapply(outcome_cols,
       function(x) {
         print(x)
         y <- tlearner_bart(x.train_treat = cate_survey_df %>% 
                            filter(condition == 'treat') %>%
                            select(-outcome_cols) %>%
                            select(-condition),
                            y.train_treat = cate_survey_df %>% 
                              filter(condition == 'treat') %>%
                              .[[x]],
                            x.train_control = cate_survey_df %>% 
                            filter(condition == 'control') %>%
                            select(-outcome_cols) %>%
                              select(-condition),
                            y.train_control = cate_survey_df %>% 
                              filter(condition == 'control') %>%
                              .[[x]],
                            x.test = cate_survey_df %>%
                              filter(condition != 'pure_control')
         )
         return(y)
       }
       )

cate_estimates_tbl <- cate_estimates %>%
  as_tibble() %>%
  rename(PANAS = panas,
        `PANAS Neg` = panas_neg,
        `PANAS Pos` = panas_pos,
        `3rd Order` = third_order,
        `Change in IH` = delta_ih,
        # `Aff. Pol.` = affective_polarization,
        `Extrem. delta` = extremity_post_less_pre)

cate_full_df <- cate_survey_df_original_names %>%
  filter(condition != 'pure_control') %>%
  bind_cols(cate_estimates_tbl)


cate_plot <- function(cate_df, conditional, fill_label, scatter = FALSE) {
  if(scatter) {
    p <- cate_full_df %>%
      pivot_longer(colnames(cate_estimates_tbl)) %>%
      ggplot(.) +
      geom_point(aes(x = !!as.symbol(conditional), y = value), alpha = 0.2, color = 'grey') +
      geom_smooth(aes(x = !!as.symbol(conditional), y = value)) +
      geom_hline(yintercept = 0, linetype = 'dashed', color = 'red') +
      labs(y = 'CATE',
             x = fill_label,
             title = paste0('CATEs by ', fill_label)) +
      facet_grid(~name, scales = 'free')
  }
  else {
    p <- cate_df %>%
      pivot_longer(cols = colnames(cate_estimates_tbl)) %>%
      ggplot(.) +
      geom_boxplot(aes(x = !!as.symbol(conditional), y = value)) +
      facet_grid(.~name, scales = 'free_y') +
        labs(y = 'CATE',
             x = fill_label,
             title = paste0('CATEs by ', fill_label)) +
        geom_hline(yintercept = 0, linetype = 'dashed') 
     
  cate_df %>%
    group_by(!!as.symbol(conditional)) %>%
    summarise_at(.vars = colnames(cate_estimates_tbl), .funs = mean) %>%
    pander::pander(caption = paste0('CATEs by subgroup: ', fill_label))
  }
  p <- p + theme(axis.text.x = element_text(angle = 90))
  print(p)
}
```

```{r plot cates, echo=FALSE, message=FALSE, warning=FALSE}
cate_plot(cate_full_df, 'pre_ih', 'Pre-treatment IH', scatter = TRUE)
cate_plot(cate_full_df, 'age', 'Age', scatter = TRUE)
cate_plot(cate_full_df, 'social_media_high', 'High social media')
cate_plot(cate_full_df %>% mutate(pid7 = factor(pid7,
                                                levels = c('Strong Democrat',
                                                           'Weak Democrat',
                                                           'Lean Democrat',
                                                           'True Independent/Other',
                                                           'Lean Republican',
                                                           'Weak Republican',
                                                           'Strong Republican'))), 'pid7', 'Political identity')
cate_plot(cate_full_df, 'pid_extremity', 'Pre-treatment Extremity via Ideology', scatter = TRUE)
cate_plot(cate_full_df, 'extremity_pre', 'Pre-treatment Extremity', scatter = TRUE)
cate_plot(cate_full_df, 'pre_policy_gc_binary', 'Pre-treatment Pro (?) Gun Control')
cate_plot(cate_full_df, 'pre_policy_imm_binary', 'Pre-treatment Pro (?) Immigration')
cate_plot(cate_full_df, 'pid3', 'Political Identity')
cate_plot(cate_full_df %>%
            mutate(ideo7 = factor(ideo7, 
                                  levels = c('Extremely conservative',
                                             'Conservative',
                                             'Somewhat conservative',
                                             'Moderate or middle of the road',
                                             'Somewhat liberal',
                                             'Liberal',
                                             'Extremely liberal'))), 'ideo7', 'Political Ideology')

cate_plot(cate_full_df %>%
            mutate(bots = factor(bots,
                                 levels = c('No, I did not encounter any bots',
                                            'Yes, I encountered one or two bots',
                                            'Yes, I encountered several bots',
                                            'Yes, I encountered many bots'))), 'bots', 'Bot perception')

# ggplot(survey_df) +
#   geom_histogram(aes(x = pid7, fill = condition))
# 
# hist(survey_df %>% filter(pid7_num == 0) %>% pull(ideo7) %>% as.factor(.))
# 
# ggplot(survey_df %>% filter(pid7_num == 0) ) +
#   geom_histogram(aes(x = ideo7), stat = 'count') +
#   coord_flip()

```



```{r}
main_hypothesis_test(survey_df, 'sent', display_plot = TRUE, title = 'All participants')
main_hypothesis_test(survey_df, 'sent_pos', display_plot = TRUE, title = 'All participants')
main_hypothesis_test(survey_df, 'sent_neg', display_plot = TRUE, title = 'All participants')

survey_df %>%
  group_by(desc_platform_toxic, condition) %>%
  summarize(sentiment = mean(sent),
            sd_sent = sd(sent),
            n_sent = n()) %>%
  mutate(desc_platform_toxic = factor(desc_platform_toxic, levels = c('Not at all',
                                                                            'Very little',
                                                                            'Some',
                                                                            'Quite a bit',
                                                                            'A great deal'))) %>%
  mutate(lower = sentiment - 1.96 * sd_sent/sqrt(n_sent),
         upper = sentiment + 1.96 * sd_sent/sqrt(n_sent)) %>%
  ggplot(.) +
  geom_errorbar(aes(x = desc_platform_toxic, ymin = lower, ymax = upper), position = 'dodge') +
  geom_point(aes(x = desc_platform_toxic, y = sentiment), position = 'dodge') +
  geom_line(aes(x = desc_platform_toxic, y = sentiment, group = 'condition'), position = 'dodge') +
  geom_hline(yintercept = 0, linetype = 'dashed') +
  facet_wrap(~condition) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(y = 'sentiment')
  
```






```{r}
cate_full_df %>%
  pivot_longer(cols = c(`PANAS`, `PANAS Neg`, `PANAS Pos`, `3rd Order`, `Change in IH`)) %>%
  ggplot(.) +
  geom_point(aes(x = age, y = value, color = name), alpha = 0.3) +
  geom_smooth(aes(x = age, y = value, color = name), se = TRUE) +
  geom_hline(yintercept = 0, color = 'black') +
  facet_grid(name~., scales = 'free_y')
```





