---
title: "Main Manuscript Figure 3 Analysis and Visualization"
author: "Austin van Loon and Srikar Katta"
date: "`r Sys.Date()`"
output: 
  rmdformats::readthedown
---

# LOADING PACKAGES.
```{r setup, include=FALSE}
rm(list = ls())
library(tidyverse)
library(ggplot2)
library(ggpubr)
library(stringr)
library(extrafont)
loadfonts(device = "win")

theme_set(theme_bw() + theme(text = element_text(size = 15)))
knitr::opts_chunk$set(echo = TRUE)
```

# LOAD IN DATA.
```{r LOAD IN DATA}
# Create dataframe "data" which contains cleaned participant data without pure controls.
data <- read_csv('../Data/data_cleaned.csv') # Read csv data file.
```

# STANDARDIZE VARIABLES.
```{r STANDARDIZE VARIABLES}
# Standardize ih_a_all.
data <- data %>% 
  mutate(ih_a_all = scale(ih_a_all))

# Standardize delta_ih.
data <- data %>% 
  mutate(delta_ih = scale(delta_ih))

# Standardize ih_engagement.
data <- data %>% 
  mutate(ih_engagement = scale(ih_engagement))

# Standardize panas_pos.
data <- data %>% 
  mutate(panas_pos = scale(panas_pos))

# Standardize panas_neg.
data <- data %>% 
  mutate(panas_neg = scale(panas_neg))

# Standardize panas.
data <- data %>% 
  mutate(panas = scale(panas))

# Standardize affective_polarization.
data <- data %>% 
  mutate(affective_polarization = scale(affective_polarization))

# Standardize extremity_post_less_pre.
data <- data %>% 
  mutate(extremity_post_less_pre = scale(extremity_post_less_pre))
```


# N-VALUES FOR EACH OUTCOME.
```{r N-VALUES FOR EACH OUTCOME}
# Void out the one participant who didn't fully answer intellectual humility measures.
data$delta_ih[data$participant_code == "9paveb"] <- NA

# Create a list of the main outcomes of interest.
outcomes <- c("ih_a_all", # Language in posts and comments indicative of humility.
              "delta_ih", # Change in self-reported humility.
              "ih_engagement", # Liked and disliked humble content.
              "panas_pos", # Positive emotional index.
              "panas_neg", # Negative emotional index.
              "panas", # Composite emotional index.
              "affective_polarization", # Change in affective polarization.
              "extremity_post_less_pre") # Moderation of focal policy position.
            
# Standardize the outcome measures. Subtract the mean of the outcome from each observation within the column, and divide by the standard deviation of the column.
for (y in outcomes){ # Run the following line of code for each column listed in the "outcomes" list.
  data[[y]] <- (data[[y]] - mean(data[[y]], na.rm=TRUE)) / sd(data[[y]], na.rm = TRUE)} # Subtract the mean of the outcome from each observation within the column, and divide by the standard deviation of the column.

# Find the n-value (number of observations) for each column.
for(y in outcomes){ # Run the following two lines of code for each column listed in the "outcomes" list.
  length <- length(data[[y]]) - sum(is.na(data[[y]])) # Create variable "length" which contains the number of observations (length(data[[y]])) within the column subtracted by the number of NA values within the column (sum(is.na(data[[y]]))).
  print(paste(y, length))} # Paste together and print the name of the column and the number of observations within the column.
```

# INTELLECTUAL HUMILITY BOOTSTRAP ANALYSIS: LANGUAGE IN POSTS AND COMMENTS INDICATIVE OF HUMILITY.
```{r INTELLECTUAL HUMILITY BOOTSTRAP ANALYSIS: LANGUAGE IN POSTS AND COMMENTS INDICATIVE OF HUMILITY}
# Set seed for analysis.
set.seed(8675309)

# Set the number of bootstrap samples.
n_boots <- 25000

# Create a new dataframe "data_ih_language" where NAs are excluded.
data_ih_language <- subset(data, !is.na(ih_a_all))

# Calculate the mean "ih_a_all" score for participants in the treatment condition.
mean_treatment <- mean(data_ih_language %>%
                       filter(condition == "treat") %>% # Within the dataframe, filter for participants in the treatment condition.
                       pull("ih_a_all")) # Select the "ih_a_all" column to take the mean of.
                          
# Calculate the mean "ih_a_all" score for participants in the control condition.
mean_control <- mean(data_ih_language %>% 
                       filter(condition == "control") %>% # Within the dataframe, filter for participants in the control condition.
                       pull("ih_a_all")) # Select the "ih_a_all" column to take the mean of.
  
# Calculate the difference "ih_langauge_beta" between the treatment and control means.
ih_langauge_beta <- mean_treatment - mean_control

# Bootstrapping.
boots <- replicate(n_boots, { # Run the following two lines of code 10,000 times (n_boots = 10000).
    boot <- data_ih_language %>% sample_frac(1, replace = TRUE) # Randomly sample all rows in the dataframe with replacement.
    mean(boot %>% filter(condition == "treat") %>% pull("ih_a_all")) - mean(boot %>% filter(condition == "control") %>% pull("ih_a_all"))}) # Calculate difference between mean treatment "ih_a_all" and mean control "ih_a_all".
  
# Calculate a 95% confidence interval for the bootstraps.
ci_95 <- quantile(boots, probs = c(0.025, 0.975)) # Save the 2.5th (lower bound) and 97.5th (upper bound) percentile of the bootstraps.

# Calculate a 90% confidence interval for the bootstraps.
ci_90 <- quantile(boots, probs = c(0.05, 0.95)) # Save the 5th (lower bound) and 95th (upper bound) percentile of the bootstraps.

# Save the 90% and 95% confidence interval lower (lo) and upper (hi) bounds. These will be used when creating Figure 3.
ih_langauge_ci_95_lo <- c(round(ci_95[1], 4)) # Round to 4 digits.
ih_langauge_ci_95_hi <- c(round(ci_95[2], 4)) # Round to 4 digits.
ih_langauge_ci_90_lo <- c(round(ci_90[1], 4)) # Round to 4 digits.
ih_langauge_ci_90_hi <- c(round(ci_90[2], 4)) # Round to 4 digits.

# Run a t-test on ih_a_all score between treatment and control groups.
t_test <- t.test(data_ih_language %>% filter(condition == "treat") %>% pull("ih_a_all"), # Compare treatment and condition groups, with "ih_a_all" as the dependent variable.
                 data_ih_language %>% filter(condition == "control") %>% pull("ih_a_all"), 
                 var.equal = TRUE, na.action = na.omit)

# Save the p-value of the t-test, which will be used when creating Figure 3.
ih_langauge_p_value <- t_test$p.value
  
# Print results.
print(c("ih_langauge_beta", ih_langauge_beta))
print(c("ih_langauge_ci_95_lo",ih_langauge_ci_95_lo[[1]]))
print(c("ih_langauge_ci_95_hi", ih_langauge_ci_95_hi[[1]]))
print(c("ih_langauge_ci_90_lo", ih_langauge_ci_90_lo[[1]]))
print(c("ih_langauge_ci_90_hi", ih_langauge_ci_90_hi[[1]]))
print(c("ih_langauge_p_value", ih_langauge_p_value))

# Remove unnecessary dataframes/vectors.
rm(n_boots, data_ih_language, mean_treatment, mean_control, boots, ci_95, ci_90, t_test)
```

# INTELLECTUAL HUMILITY BOOTSTRAP ANALYSIS: CHANGE IN SELF-REPORTED HUMILITY.
```{r INTELLECTUAL HUMILITY BOOTSTRAP ANALYSIS: CHANGE IN SELF-REPORTED HUMILITY}
# Set seed for analysis.
set.seed(8675309)

# Set the number of bootstrap samples.
n_boots <- 25000

# Create dataframe "data_delta_ih" which does not contain the participant who didn't answer the intellectual humility measures.
data_delta_ih <- data[data$participant_code != "9paveb", ]

# Calculate the mean "delta_ih" score for participants in the treatment condition.
mean_treatment <- mean(data_delta_ih %>%
                       filter(condition == "treat") %>% # Within the dataframe, filter for participants in the treatment condition.
                       pull("delta_ih")) # Select the "delta_ih" column to take the mean of.
                          
# Calculate the mean "delta_ih" score for participants in the control condition.
mean_control <- mean(data_delta_ih %>% 
                       filter(condition == "control") %>% # Within the dataframe, filter for participants in the control condition.
                       pull("delta_ih")) # Select the "delta_ih" column to take the mean of.
  
# Calculate the difference "delta_ih_beta" between the treatment and control means.
delta_ih_beta <- mean_treatment - mean_control

# Bootstrapping.
boots <- replicate(n_boots, { # Run the following two lines of code 10,000 times (n_boots = 10000).
    boot <- data_delta_ih %>% sample_frac(1, replace = TRUE) # Randomly sample all rows in the dataframe with replacement.
    mean(boot %>% filter(condition == "treat") %>% pull("delta_ih")) - mean(boot %>% filter(condition == "control") %>% pull("delta_ih"))}) # Calculate difference between mean treatment "delta_ih" and mean control "delta_ih".
  
# Calculate a 95% confidence interval for the bootstraps.
ci_95 <- quantile(boots, probs = c(0.025, 0.975)) # Save the 2.5th (lower bound) and 97.5th (upper bound) percentile of the bootstraps.

# Calculate a 90% confidence interval for the bootstraps.
ci_90 <- quantile(boots, probs = c(0.05, 0.95)) # Save the 5th (lower bound) and 95th (upper bound) percentile of the bootstraps.

# Save the 90% and 95% confidence interval lower (lo) and upper (hi) bounds. These will be used when creating Figure 3.
delta_ih_ci_95_lo <- c(round(ci_95[1], 4)) # Round to 4 digits.
delta_ih_ci_95_hi <- c(round(ci_95[2], 4)) # Round to 4 digits.
delta_ih_ci_90_lo <- c(round(ci_90[1], 4)) # Round to 4 digits.
delta_ih_ci_90_hi <- c(round(ci_90[2], 4)) # Round to 4 digits.

# Run a t-test on delta_ih score between treatment and control groups.
t_test <- t.test(data_delta_ih %>% filter(condition == "treat") %>% pull("delta_ih"), # Compare treatment and condition groups, with "delta_ih" as the dependent variable.
                 data_delta_ih %>% filter(condition == "control") %>% pull("delta_ih"),
                 var.equal = TRUE, na.action = na.omit)

# Save the p-value of the t-test, which will be used when creating Figure 3.
delta_ih_p_value <- t_test$p.value
  
# Print results.
print(c("delta_ih_beta", delta_ih_beta))
print(c("delta_ih_ci_95_lo", delta_ih_ci_95_lo[[1]]))
print(c("delta_ih_ci_95_hi", delta_ih_ci_95_hi[[1]]))
print(c("delta_ih_ci_90_lo", delta_ih_ci_90_lo[[1]]))
print(c("delta_ih_ci_90_hi", delta_ih_ci_90_hi[[1]]))
print(c("delta_ih_p_value", delta_ih_p_value))

# Remove unnecessary dataframes/vectors.
rm(n_boots, data_delta_ih, mean_treatment, mean_control, boots, ci_95, ci_90, t_test)

```

# INTELLECTUAL HUMILITY BOOTSTRAP ANALYSIS: LIKED AND DISLIKED HUMBLE CONTENT.
```{r INTELLECTUAL HUMILITY BOOTSTRAP ANALYSIS: LIKED AND DISLIKED HUMBLE CONTENT}
# Set seed for analysis.
set.seed(8675309)

# Set the number of bootstrap samples.
n_boots <- 25000

# Calculate the mean "ih_engagement" score for participants in the treatment condition.
mean_treatment <- mean(data %>%
                       filter(condition == "treat") %>% # Within the dataframe, filter for participants in the treatment condition.
                       pull("ih_engagement")) # Select the "ih_engagement" column to take the mean of.
                          
# Calculate the mean "ih_engagement" score for participants in the control condition.
mean_control <- mean(data %>% 
                       filter(condition == "control") %>% # Within the dataframe, filter for participants in the control condition.
                       pull("ih_engagement")) # Select the "ih_engagement" column to take the mean of.
  
# Calculate the difference "ih_engagement_beta" between the treatment and control means.
ih_engagement_beta <- mean_treatment - mean_control

# Bootstrapping.
boots <- replicate(n_boots, { # Run the following two lines of code 10,000 times (n_boots = 10000).
    boot <- data %>% sample_frac(1, replace = TRUE) # Randomly sample all rows in the dataframe with replacement.
    mean(boot %>% filter(condition == "treat") %>% pull("ih_engagement")) - mean(boot %>% filter(condition == "control") %>% pull("ih_engagement"))}) # Calculate difference between mean treatment "ih_engagement" and mean control "ih_engagement".
  
# Calculate a 95% confidence interval for the bootstraps.
ci_95 <- quantile(boots, probs = c(0.025, 0.975)) # Save the 2.5th (lower bound) and 97.5th (upper bound) percentile of the bootstraps.

# Calculate a 90% confidence interval for the bootstraps.
ci_90 <- quantile(boots, probs = c(0.05, 0.95)) # Save the 5th (lower bound) and 95th (upper bound) percentile of the bootstraps.

# Save the 90% and 95% confidence interval lower (lo) and upper (hi) bounds. These will be used when creating Figure 3.
ih_engagement_ci_95_lo <- c(round(ci_95[1], 4)) # Round to 4 digits.
ih_engagement_ci_95_hi <- c(round(ci_95[2], 4)) # Round to 4 digits.
ih_engagement_ci_90_lo <- c(round(ci_90[1], 4)) # Round to 4 digits.
ih_engagement_ci_90_hi <- c(round(ci_90[2], 4)) # Round to 4 digits.

# Run a t-test on ih_engagement score between treatment and control groups.
t_test <- t.test(data %>% filter(condition == "treat") %>% pull("ih_engagement"), # Compare treatment and condition groups, with "ih_engagement" as the dependent variable.
                 data %>% filter(condition == "control") %>% pull("ih_engagement"),
                 var.equal = TRUE, na.action = na.omit)

# Save the p-value of the t-test, which will be used when creating Figure 3.
ih_engagement_p_value <- t_test$p.value

# Print results.
print(c("ih_engagement_beta", ih_engagement_beta))
print(c("ih_engagement_ci_95_lo", ih_engagement_ci_95_lo[[1]]))
print(c("ih_engagement_ci_95_hi", ih_engagement_ci_95_hi[[1]]))
print(c("ih_engagement_ci_90_lo", ih_engagement_ci_90_lo[[1]]))
print(c("ih_engagement_ci_90_hi", ih_engagement_ci_90_hi[[1]]))
print(c("ih_engagement_p_value", ih_engagement_p_value))

# Remove unnecessary dataframes/vectors.
rm(n_boots, mean_treatment, mean_control, boots, ci_95, ci_90, t_test)

```

# EMOTIONAL EXPERIENCE BOOTSTRAP ANALYSIS: POSITIVE EMOTIONAL INDEX.
```{r EMOTIONAL EXPERIENCE BOOTSTRAP ANALYSIS: POSITIVE EMOTIONAL INDEX}
# Set seed for analysis.
set.seed(8675309)

# Set the number of bootstrap samples.
n_boots <- 25000

# Calculate the mean "panas_pos" score for participants in the treatment condition.
mean_treatment <- mean(data %>%
                       filter(condition == "treat") %>% # Within the dataframe, filter for participants in the treatment condition.
                       pull("panas_pos")) # Select the "panas_pos" column to take the mean of.
                          
# Calculate the mean "panas_pos" score for participants in the control condition.
mean_control <- mean(data %>% 
                       filter(condition == "control") %>% # Within the dataframe, filter for participants in the control condition.
                       pull("panas_pos")) # Select the "panas_pos" column to take the mean of.
  
# Calculate the difference "panas_pos_beta" between the treatment and control means.
panas_pos_beta <- mean_treatment - mean_control

# Bootstrapping.
boots <- replicate(n_boots, { # Run the following two lines of code 10,000 times (n_boots = 10000).
    boot <- data %>% sample_frac(1, replace = TRUE) # Randomly sample all rows in the dataframe with replacement.
    mean(boot %>% filter(condition == "treat") %>% pull("panas_pos")) - mean(boot %>% filter(condition == "control") %>% pull("panas_pos"))}) # Calculate difference between mean treatment "panas_pos" and mean control "panas_pos".
  
# Calculate a 95% confidence interval for the bootstraps.
ci_95 <- quantile(boots, probs = c(0.025, 0.975)) # Save the 2.5th (lower bound) and 97.5th (upper bound) percentile of the bootstraps.

# Calculate a 90% confidence interval for the bootstraps.
ci_90 <- quantile(boots, probs = c(0.05, 0.95)) # Save the 5th (lower bound) and 95th (upper bound) percentile of the bootstraps.

# Save the 90% and 95% confidence interval lower (lo) and upper (hi) bounds. These will be used when creating Figure 3.
panas_pos_ci_95_lo <- c(round(ci_95[1], 4)) # Round to 4 digits.
panas_pos_ci_95_hi <- c(round(ci_95[2], 4)) # Round to 4 digits.
panas_pos_ci_90_lo <- c(round(ci_90[1], 4)) # Round to 4 digits.
panas_pos_ci_90_hi <- c(round(ci_90[2], 4)) # Round to 4 digits.

# Run a t-test on panas_pos score between treatment and control groups.
t_test <- t.test(data %>% filter(condition == "treat") %>% pull("panas_pos"), # Compare treatment and condition groups, with "panas_pos" as the dependent variable.
                 data %>% filter(condition == "control") %>% pull("panas_pos"),
                 var.equal = TRUE, na.action = na.omit)

# Save the p-value of the t-test, which will be used when creating Figure 3.
panas_pos_p_value <- t_test$p.value
  
# Print results.
print(c("panas_pos_beta", panas_pos_beta))
print(c("panas_pos_ci_95_lo", panas_pos_ci_95_lo[[1]]))
print(c("panas_pos_ci_95_hi", panas_pos_ci_95_hi[[1]]))
print(c("panas_pos_ci_90_lo", panas_pos_ci_90_lo[[1]]))
print(c("panas_pos_ci_90_hi", panas_pos_ci_90_hi[[1]]))
print(c("panas_pos_p_value", panas_pos_p_value))

# Remove unnecessary dataframes/vectors.
rm(n_boots, mean_treatment, mean_control, boots, ci_95, ci_90, t_test)
```

# EMOTIONAL EXPERIENCE BOOTSTRAP ANALYSIS: NEGATIVE EMOTIONAL INDEX.
```{r EMOTIONAL EXPERIENCE BOOTSTRAP ANALYSIS: NEGATIVE EMOTIONAL INDEX}
# Set seed for analysis.
set.seed(8675309)

# Set the number of bootstrap samples.
n_boots <- 25000

# Calculate the mean "panas_neg" score for participants in the treatment condition.
mean_treatment <- mean(data %>%
                       filter(condition == "treat") %>% # Within the dataframe, filter for participants in the treatment condition.
                       pull("panas_neg")) # Select the "panas_neg" column to take the mean of.
                          
# Calculate the mean "panas_neg" score for participants in the control condition.
mean_control <- mean(data %>% 
                       filter(condition == "control") %>% # Within the dataframe, filter for participants in the control condition.
                       pull("panas_neg")) # Select the "panas_neg" column to take the mean of.
  
# Calculate the difference "panas_neg_beta" between the treatment and control means.
panas_neg_beta <- mean_treatment - mean_control

# Bootstrapping.
boots <- replicate(n_boots, { # Run the following two lines of code 10,000 times (n_boots = 10000).
    boot <- data %>% sample_frac(1, replace = TRUE) # Randomly sample all rows in the dataframe with replacement.
    mean(boot %>% filter(condition == "treat") %>% pull("panas_neg")) - mean(boot %>% filter(condition == "control") %>% pull("panas_neg"))}) # Calculate difference between mean treatment "panas_neg" and mean control "panas_neg".
  
# Calculate a 95% confidence interval for the bootstraps.
ci_95 <- quantile(boots, probs = c(0.025, 0.975)) # Save the 2.5th (lower bound) and 97.5th (upper bound) percentile of the bootstraps.

# Calculate a 90% confidence interval for the bootstraps.
ci_90 <- quantile(boots, probs = c(0.05, 0.95)) # Save the 5th (lower bound) and 95th (upper bound) percentile of the bootstraps.

# Save the 90% and 95% confidence interval lower (lo) and upper (hi) bounds. These will be used when creating Figure 3.
panas_neg_ci_95_lo <- c(round(ci_95[1], 4)) # Round to 4 digits.
panas_neg_ci_95_hi <- c(round(ci_95[2], 4)) # Round to 4 digits.
panas_neg_ci_90_lo <- c(round(ci_90[1], 4)) # Round to 4 digits.
panas_neg_ci_90_hi <- c(round(ci_90[2], 4)) # Round to 4 digits.

# Run a t-test on panas_neg score between treatment and control groups.
t_test <- t.test(data %>% filter(condition == "treat") %>% pull("panas_neg"), # Compare treatment and condition groups, with "panas_neg" as the dependent variable.
                 data %>% filter(condition == "control") %>% pull("panas_neg"),
                 var.equal = TRUE, na.action = na.omit)

# Save the p-value of the t-test, which will be used when creating Figure 3.
panas_neg_p_value <- t_test$p.value

# Print results.
print(c("panas_neg_beta", panas_neg_beta))
print(c("panas_neg_ci_95_lo", panas_neg_ci_95_lo[[1]]))
print(c("panas_neg_ci_95_hi", panas_neg_ci_95_hi[[1]]))
print(c("panas_neg_ci_90_lo", panas_neg_ci_90_lo[[1]]))
print(c("panas_neg_ci_90_hi", panas_neg_ci_90_hi[[1]]))
print(c("panas_neg_p_value", panas_neg_p_value))

# Remove unnecessary dataframes/vectors.
rm(n_boots, mean_treatment, mean_control, boots, ci_95, ci_90, t_test)
```

# EMOTIONAL EXPERIENCE BOOTSTRAP ANALYSIS: COMPOSITE EMOTIONAL INDEX.
```{r EMOTIONAL EXPERIENCE BOOTSTRAP ANALYSIS: COMPOSITE EMOTIONAL INDEX}
# Set seed for analysis.
set.seed(8675309)

# Set the number of bootstrap samples.
n_boots <- 25000

# Calculate the mean "panas" score for participants in the treatment condition.
mean_treatment <- mean(data %>%
                       filter(condition == "treat") %>% # Within the dataframe, filter for participants in the treatment condition.
                       pull("panas")) # Select the "panas" column to take the mean of.
                          
# Calculate the mean "panas" score for participants in the control condition.
mean_control <- mean(data %>% 
                       filter(condition == "control") %>% # Within the dataframe, filter for participants in the control condition.
                       pull("panas")) # Select the "panas" column to take the mean of.
  
# Calculate the difference "panas_beta" between the treatment and control means.
panas_beta <- mean_treatment - mean_control

# Bootstrapping.
boots <- replicate(n_boots, { # Run the following two lines of code 10,000 times (n_boots = 10000).
    boot <- data %>% sample_frac(1, replace = TRUE) # Randomly sample all rows in the dataframe with replacement.
    mean(boot %>% filter(condition == "treat") %>% pull("panas")) - mean(boot %>% filter(condition == "control") %>% pull("panas"))}) # Calculate difference between mean treatment "panas" and mean control "panas".
  
# Calculate a 95% confidence interval for the bootstraps.
ci_95 <- quantile(boots, probs = c(0.025, 0.975)) # Save the 2.5th (lower bound) and 97.5th (upper bound) percentile of the bootstraps.

# Calculate a 90% confidence interval for the bootstraps.
ci_90 <- quantile(boots, probs = c(0.05, 0.95)) # Save the 5th (lower bound) and 95th (upper bound) percentile of the bootstraps.

# Save the 90% and 95% confidence interval lower (lo) and upper (hi) bounds. These will be used when creating Figure 3.
panas_ci_95_lo <- c(round(ci_95[1], 4)) # Round to 4 digits.
panas_ci_95_hi <- c(round(ci_95[2], 4)) # Round to 4 digits.
panas_ci_90_lo <- c(round(ci_90[1], 4)) # Round to 4 digits.
panas_ci_90_hi <- c(round(ci_90[2], 4)) # Round to 4 digits.

# Run a t-test on panas score between treatment and control groups.
t_test <- t.test(data %>% filter(condition == "treat") %>% pull("panas"), # Compare treatment and condition groups, with "panas" as the dependent variable.
                 data %>% filter(condition == "control") %>% pull("panas"),
                 var.equal = TRUE, na.action = na.omit)

# Save the p-value of the t-test, which will be used when creating Figure 3.
panas_p_value <- t_test$p.value

# Print results.
print(c("panas_beta", panas_beta))
print(c("panas_ci_95_lo", panas_ci_95_lo[[1]]))
print(c("panas_ci_95_hi", panas_ci_95_hi[[1]]))
print(c("panas_ci_90_lo", panas_ci_90_lo[[1]]))
print(c("panas_ci_90_hi", panas_ci_90_hi[[1]]))
print(c("panas_p_value", panas_p_value))
  
# Remove unnecessary dataframes/vectors.
rm(n_boots, mean_treatment, mean_control, boots, ci_95, ci_90, t_test)
```

# POLITICAL ATTITUDES BOOTSTRAP ANALYSIS: CHANGE IN AFFECTIVE POLARIZATION.
```{r POLITICAL ATTITUDES BOOTSTRAP ANALYSIS: CHANGE IN AFFECTIVE POLARIZATION}
# Set seed for analysis.
set.seed(8675309)

# Set the number of bootstrap samples.
n_boots <- 25000

# Create dataframe "data_ap" which does not contain the participant who identified as "Pure Independents".
data_ap <- subset(data, pid7 != "Pure Independent")

# Calculate the mean "affective_polarization" score for participants in the treatment condition.
mean_treatment <- mean(data_ap %>%
                       filter(condition == "treat") %>% # Within the dataframe, filter for participants in the treatment condition.
                       pull("affective_polarization")) # Select the "affective_polarization" column to take the mean of.
                          
# Calculate the mean "affective_polarization" score for participants in the control condition.
mean_control <- mean(data_ap %>% 
                       filter(condition == "control") %>% # Within the dataframe, filter for participants in the control condition.
                       pull("affective_polarization")) # Select the "affective_polarization" column to take the mean of.
  
# Calculate the difference "delta_ih_beta" between the treatment and control means.
affective_polarization_beta <- mean_treatment - mean_control

# Bootstrapping.
boots <- replicate(n_boots, { # Run the following two lines of code 10,000 times (n_boots = 10000).
    boot <- data_ap %>% sample_frac(1, replace = TRUE) # Randomly sample all rows in the dataframe with replacement.
    mean(boot %>% filter(condition == "treat") %>% pull("affective_polarization")) - mean(boot %>% filter(condition == "control") %>% pull("affective_polarization"))}) # Calculate difference between mean treatment "affective_polarization" and mean control "affective_polarization".
  
# Calculate a 95% confidence interval for the bootstraps.
ci_95 <- quantile(boots, probs = c(0.025, 0.975)) # Save the 2.5th (lower bound) and 97.5th (upper bound) percentile of the bootstraps.

# Calculate a 90% confidence interval for the bootstraps.
ci_90 <- quantile(boots, probs = c(0.05, 0.95)) # Save the 5th (lower bound) and 95th (upper bound) percentile of the bootstraps.

# Save the 90% and 95% confidence interval lower (lo) and upper (hi) bounds. These will be used when creating Figure 3.
affective_polarization_ci_95_lo <- c(round(ci_95[1], 4)) # Round to 4 digits.
affective_polarization_ci_95_hi <- c(round(ci_95[2], 4)) # Round to 4 digits.
affective_polarization_ci_90_lo <- c(round(ci_90[1], 4)) # Round to 4 digits.
affective_polarization_ci_90_hi <- c(round(ci_90[2], 4)) # Round to 4 digits.

# Run a t-test on affective_polarization score between treatment and control groups.
t_test <- t.test(data_ap %>% filter(condition == "treat") %>% pull("affective_polarization"), # Compare treatment and condition groups, with "affective_polarization" as the dependent variable.
                 data_ap %>% filter(condition == "control") %>% pull("affective_polarization"),
                 var.equal = TRUE, na.action = na.omit)

# Save the p-value of the t-test, which will be used when creating Figure 3.
affective_polarization_p_value <- t_test$p.value
  
# Print results.
print(c("affective_polarization_beta", affective_polarization_beta))
print(c("affective_polarization_ci_95_lo", affective_polarization_ci_95_lo[[1]]))
print(c("affective_polarization_ci_95_hi", affective_polarization_ci_95_hi[[1]]))
print(c("affective_polarization_ci_90_lo", affective_polarization_ci_90_lo[[1]]))
print(c("affective_polarization_ci_90_hi", affective_polarization_ci_90_hi[[1]]))
print(c("affective_polarization_p_value", affective_polarization_p_value))

# Remove unnecessary dataframes/vectors.
rm(n_boots, data_ap, mean_treatment, mean_control, boots, ci_95, ci_90, t_test)

```

# POLITICAL ATTITUDES BOOTSTRAP ANALYSIS: MODERATION OF FOCAL POLICY POSITION.
```{r POLITICAL ATTITUDES BOOTSTRAP ANALYSIS: MODERATION OF FOCAL POLICY POSITION}
# Set seed for analysis.
set.seed(8675309)

# Set the number of bootstrap samples.
n_boots <- 25000

# Calculate the mean "extremity_post_less_pre" score for participants in the treatment condition.
mean_treatment <- mean(data %>%
                       filter(condition == "treat") %>% # Within the dataframe, filter for participants in the treatment condition.
                       pull("extremity_post_less_pre")) # Select the "extremity_post_less_pre" column to take the mean of.
                          
# Calculate the mean "extremity_post_less_pre" score for participants in the control condition.
mean_control <- mean(data %>% 
                       filter(condition == "control") %>% # Within the dataframe, filter for participants in the control condition.
                       pull("extremity_post_less_pre")) # Select the "extremity_post_less_pre" column to take the mean of.
  
# Calculate the difference "extremity_post_less_pre_beta" between the treatment and control means.
extremity_post_less_pre_beta <- mean_treatment - mean_control

# Bootstrapping.
boots <- replicate(n_boots, { # Run the following two lines of code 10,000 times (n_boots = 10000).
    boot <- data %>% sample_frac(1, replace = TRUE) # Randomly sample all rows in the dataframe with replacement.
    mean(boot %>% filter(condition == "treat") %>% pull("extremity_post_less_pre")) - mean(boot %>% filter(condition == "control") %>% pull("extremity_post_less_pre"))}) # Calculate difference between mean treatment "extremity_post_less_pre" and mean control "extremity_post_less_pre".
  
# Calculate a 95% confidence interval for the bootstraps.
ci_95 <- quantile(boots, probs = c(0.025, 0.975)) # Save the 2.5th (lower bound) and 97.5th (upper bound) percentile of the bootstraps.

# Calculate a 90% confidence interval for the bootstraps.
ci_90 <- quantile(boots, probs = c(0.05, 0.95)) # Save the 5th (lower bound) and 95th (upper bound) percentile of the bootstraps.

# Save the 90% and 95% confidence interval lower (lo) and upper (hi) bounds. These will be used when creating Figure 3.
extremity_post_less_pre_ci_95_lo <- c(round(ci_95[1], 4)) # Round to 4 digits.
extremity_post_less_pre_ci_95_hi <- c(round(ci_95[2], 4)) # Round to 4 digits.
extremity_post_less_pre_ci_90_lo <- c(round(ci_90[1], 4)) # Round to 4 digits.
extremity_post_less_pre_ci_90_hi <- c(round(ci_90[2], 4)) # Round to 4 digits.

# Run a t-test on extremity_post_less_pre score between treatment and control groups.
t_test <- t.test(data %>% filter(condition == "treat") %>% pull("extremity_post_less_pre"), # Compare treatment and condition groups, with "extremity_post_less_pre" as the dependent variable.
                 data %>% filter(condition == "control") %>% pull("extremity_post_less_pre"),
                 var.equal = TRUE, na.action = na.omit)

# Save the p-value of the t-test, which will be used when creating Figure 3.
extremity_post_less_pre_p_value <- t_test$p.value

# Print results.
print(c("extremity_post_less_pre_beta", extremity_post_less_pre_beta))
print(c("extremity_post_less_pre_ci_95_lo", extremity_post_less_pre_ci_95_lo[[1]]))
print(c("extremity_post_less_pre_ci_95_hi", extremity_post_less_pre_ci_95_hi[[1]]))
print(c("extremity_post_less_pre_ci_90_lo", extremity_post_less_pre_ci_90_lo[[1]]))
print(c("extremity_post_less_pre_ci_90_hi", extremity_post_less_pre_ci_90_hi[[1]]))
print(c("extremity_post_less_pre_p_value", extremity_post_less_pre_p_value))

# Remove unnecessary dataframes/vectors.
rm(n_boots, mean_treatment, mean_control, boots, ci_95, ci_90, t_test)
```


# SK: BOOTSTRAP ANALYSIS -- SIMULTANEOUS BOOTSTRAP
```{r}

# Set seed for analysis.
set.seed(8675309)

# Set the number of bootstrap samples.
n_boots <- 25000

# Bootstrapping.
boots <- replicate(n_boots, { # Run the following two lines of code 10,000 times (n_boots = 10000).
    tx <- data %>% sample_frac(1, replace = TRUE) %>% filter(condition == "treat") %>% select(outcomes) %>% apply(., 2, mean, na.rm = TRUE)
    ctrl <- data %>% sample_frac(1, replace = TRUE) %>% filter(condition == "control") %>% select(outcomes) %>% apply(., 2, mean, na.rm = TRUE)
    tx - ctrl
}) # Calculate difference between mean treatment "panas_pos" and mean control "panas_pos".
  

## compute confidence intervals from bootstrap samples
ci_df <- apply(boots, 1, function(x)
  quantile(x, probs = c(0.025, 0.05, 0.95, 0.975))) %>% # find 0.025, 0.05, 0.95, 0.975 quantiles of bootstraps for each outcome
  t() %>% # each row should represent CIs for a single outcome
  as.data.frame() %>% 
  rename( # rename percentile labels to describe how they are used in confidence interval construction
    'Lower_CI_95' = `2.5%`,
    'Lower_CI_90' = `5%`,
    'Upper_CI_90' = `95%`,
    'Upper_CI_95' = `97.5%`
  ) %>%
  mutate(label = row.names(.)) # add outcome at row level

pval_df <- sapply(outcomes, # run a t-test for each outcome and calculate p-value
                  function(x) {
                    t.test(
                      data %>% filter(condition == 'treat') %>% .[[x]],
                      data %>% filter(condition == 'control') %>% .[[x]],
                      var.equal = TRUE,
                      na.omit = TRUE
                    )$p.value
                  }
      ) %>% 
      data.frame() %>% # convert to data frame object
      rename('P.value' = '.') %>% # rename column
      mutate(label = row.names(.)) # add outcome column

coef_df <- sapply(outcomes, # calculate diff in means pt estimate for each outcome
                  function(x) {
                    tx <- data %>% filter(condition == 'treat') %>% .[[x]] %>% mean(na.rm = TRUE)
                    ctrl <- data %>% filter(condition == 'control') %>% .[[x]] %>% mean(na.rm = TRUE)
                    tx - ctrl
                  }
      ) %>% 
      data.frame() %>% # convert to data frame object
      rename('Coefficient' = '.') %>% # rename column
      mutate(label = row.names(.)) # add outcome column


data_all_outcomes <- inner_join(ci_df, pval_df, by = 'label') %>% inner_join(coef_df, by = 'label')

# what label should we use for each outcome?
label_df <- tribble(
  ~orig, ~Outcome,
  'ih_a_all', "Language in posts and comments indicative of humility",
  'delta_ih', 'Change in self-reported humility',
  'ih_engagement', 'Liked and disliked humble content',
  'panas_pos', "Positive emotional index",
  'panas_neg', "Negative emotional index",
  'panas', "Composite emotional index",
  'affective_polarization', "Change in affective polarization", 
  'extremity_post_less_pre', "Moderation of focal policy position"
)

# update outcomes and p-values
data_all_outcomes <- inner_join(data_all_outcomes, label_df, by = c('label' = 'orig')) %>%
  mutate(Color = case_when(
    P.value >=0.05 ~ "grey", # When the p-value is >=0.05, assign the color grey.
    P.value <0.05 ~ "black"))

## separate data based on outcome grouping
data_intellectual_humility <- data_all_outcomes %>% 
  filter(label %in% c('ih_a_all', 'delta_ih', 'ih_engagement'))
data_emotional_experience <- data_all_outcomes %>%
  filter(label %in% c('panas_pos', 'panas_neg', 'panas'))
data_political_attitudes <- data_all_outcomes %>%
  filter(label %in% c('affective_polarization', 'extremity_post_less_pre'))
```


# SAVE ALL ANALYSES AS DATAFRAMES.
```{r SAVE ALL ANALYSES AS DATAFRAMES}
# # Create dataframe "data_intellectual_humility" which contains all the bootstrap analyses for intellectual humility measures in one dataframe.
# data_intellectual_humility <- data.frame(
#   Outcome = factor(c("Language in posts and comments indicative of humility", # Identify the specific outcomes.
#                       "Change in self-reported humility", 
#                       "Liked and disliked humble content")),
#   Coefficient = c(ih_langauge_beta, delta_ih_beta, ih_engagement_beta), # Beta coefficients are the differences between treatment and control means.
#   Lower_CI_95 = c(ih_langauge_ci_95_lo, delta_ih_ci_95_lo, ih_engagement_ci_95_lo), # Lower bounds of the 95% confidence interval.
#   Upper_CI_95 = c(ih_langauge_ci_95_hi, delta_ih_ci_95_hi, ih_engagement_ci_95_hi), # Upper bounds of the 95% confidence interval.
#   Lower_CI_90 = c(ih_langauge_ci_90_lo, delta_ih_ci_90_lo, ih_engagement_ci_90_lo), # Lower bounds of the 90% confidence interval.
#   Upper_CI_90 = c(ih_langauge_ci_90_hi, delta_ih_ci_90_hi, ih_engagement_ci_90_hi), # Upper bounds of the 90% confidence interval.
#   P.value = c(ih_langauge_p_value, delta_ih_p_value, ih_engagement_p_value)) # P-values from the t-tests.
# 
# # Create dataframe "data_emotional_experience" which contains all the bootstrap analyses for emotional experience measures in one dataframe.
# data_emotional_experience <- data.frame(
#   Outcome = factor(c("Positive emotional index", # Identify the specific outcomes.
#                      "Negative emotional index",
#                      "Composite emotional index")),
#   Coefficient = c(panas_pos_beta, panas_neg_beta, panas_beta), # Beta coefficients are the differences between treatment and control means.
#   Lower_CI_95 = c(panas_pos_ci_95_lo, panas_neg_ci_95_lo, panas_ci_95_lo), # Lower bounds of the 95% confidence interval.
#   Upper_CI_95 = c(panas_pos_ci_95_hi, panas_neg_ci_95_hi, panas_ci_95_hi), # Upper bounds of the 95% confidence interval.
#   Lower_CI_90 = c(panas_pos_ci_90_lo, panas_neg_ci_90_lo, panas_ci_90_lo), # Lower bounds of the 90% confidence interval.
#   Upper_CI_90 = c(panas_pos_ci_90_hi, panas_neg_ci_90_hi, panas_ci_90_hi), # Upper bounds of the 90% confidence interval.
#   P.value = c(panas_pos_p_value, panas_neg_p_value, panas_p_value)) # P-values from the t-tests.
# 
# # Create dataframe "data_political_attitudes" which contains all the bootstrap analyses for political attitude measures in one dataframe.
# data_political_attitudes <- data.frame(
#   Outcome = factor(c("Change in affective polarization", # Identify the specific outcomes.
#                      "Moderation of focal policy position")),
#   Coefficient = c(affective_polarization_beta, extremity_post_less_pre_beta), # Beta coefficients are the differences between treatment and control means.
#   Lower_CI_95 = c(affective_polarization_ci_95_lo, extremity_post_less_pre_ci_95_lo), # Lower bounds of the 95% confidence interval.
#   Upper_CI_95 = c(affective_polarization_ci_95_hi, extremity_post_less_pre_ci_95_hi), # Upper bounds of the 95% confidence interval.
#   Lower_CI_90 = c(affective_polarization_ci_90_lo, extremity_post_less_pre_ci_90_lo), # Lower bounds of the 90% confidence interval.
#   Upper_CI_90 = c(affective_polarization_ci_90_hi, extremity_post_less_pre_ci_90_hi), # Upper bounds of the 90% confidence interval.
#   P.value = c(affective_polarization_p_value, extremity_post_less_pre_p_value)) # P-values from the t-tests.

# Assign color to data_intellectual_humility based off of p-value significance (black = significant, grey = not significant).
# data_intellectual_humility <- data_intellectual_humility %>% 
#   mutate(Color = case_when(
#     P.value >=0.05 ~ "grey", # When the p-value is >=0.05, assign the color grey.
#     P.value <0.05 ~ "black")) # When the p-value is <0.05, assign the color black.
# 
# # Assign color to data_emotional_experience based off of p-value significance (black = significant, grey = not significant).
# data_emotional_experience <- data_emotional_experience %>% 
#   mutate(Color = case_when(
#     P.value >=0.05 ~ "grey", # When the p-value is >=0.05, assign the color grey.
#     P.value <0.05 ~ "black")) # When the p-value is <0.05, assign the color black.
# 
# # Assign color to data_political_attitudes based off of p-value significance (black = significant, grey = not significant)
# data_political_attitudes <- data_political_attitudes %>% 
#   mutate(Color = case_when(
#     P.value >=0.05 ~ "grey", # When the p-value is >=0.05, assign the color grey.
#     P.value <0.05 ~ "black")) # When the p-value is <0.05, assign the color black.
# 
# # Final dataframes.
# print(data_intellectual_humility)
# print(data_emotional_experience)
# print(data_political_attitudes)

```

# FIGURE FORMATTING: INTELLECTUAL HUMILITY.
```{r FIGURE FORMATTING: INTELLECTUAL HUMILITY}
# Add the beta-coefficients and error bars to the graph.
figure_intellectual_humility <- ggplot(data_intellectual_humility) + # Define dataset, x, y and color variables.
  geom_point(size=8, aes(x=Coefficient, y=Outcome, color = Color), show.legend = FALSE) + # Create points on the graph for the beta-coefficients. define the size of the point as 8.
  geom_errorbarh(aes(y=Outcome, xmin=Lower_CI_90, xmax=Upper_CI_90, color = Color), # Create error bars for the 90% confidence interval.
                 linewidth=2, height = 0, show.legend = FALSE) + # Define line width as 2 and height as 0 (this ensures that the error bar is just a line with no end bars).
  geom_errorbarh(aes(y=Outcome, xmin=Lower_CI_95, xmax=Upper_CI_95, color = Color), # Create error bars for the 95% confidence interval.
                 linewidth=1, height=0, show.legend = FALSE, lineend = "round") # Define line width as 1 and height as 0 (this ensures that the error bar is just a line with no end bars).
  
# Add a dotted vertical line at 0.
figure_intellectual_humility <- figure_intellectual_humility +
  geom_vline(xintercept=0, linetype="dotted", linewidth=2)  

# Change the background colors of the graph.
figure_intellectual_humility <- figure_intellectual_humility +
  theme_minimal() # Change the background of the graph to be white with grey grid lines.

# Y-Axis.
figure_intellectual_humility <- figure_intellectual_humility +
  scale_y_discrete(limits = rev(c("Language in posts and comments indicative of humility", # Fix the order of the outcomes.
                      "Change in self-reported humility", 
                      "Liked and disliked humble content")),
                   labels = function(x) str_wrap(x, width = 20)) + # Condense the size of the outcome labels, so that they are split in 2-3 lines.
  ylab("Intellectual\nHumility") + # Title the y-axis with the outcome group ("Intellectual Humility").
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 95, b = 0, l = 0), # Define the size of the margins of the y-axis title (t = top, r = right, b = bottom, l = left).
                                    size=24, face="bold"), # Define the text size as 24, and bold the text.
        axis.text.y = element_text(margin = margin(t = 0, r = 80, b = 0, l = 0), # Define the size of the margins of the outcome labels (t = top, r = right, b = bottom, l = left).
                                   size=14, hjust = 0.5), # Define the text size as 14, and center the text.
        text = element_text(family="Verdana")) # Define the text font as "Verdana".

# X-axis.
figure_intellectual_humility <- figure_intellectual_humility + 
  scale_x_continuous(labels=NULL, limits = c(-0.26, 0.26)) + # Get rid of the x-axis labels (this is important for when the figures are stitched together), limit the x-axis between the range of -0.26 to 0.26.
  xlab(NULL) # Get rid of x-axis title.

# Colors.
figure_intellectual_humility <- figure_intellectual_humility + 
  scale_color_identity() # Ensure the colors of the points/bars are in accordance with the significance colors stated in the dataframe.

# Final intellectual humility outcomes plot.
print(figure_intellectual_humility)
```

# FIGURE FORMATTING: EMOTIONAL EXPERIENCE.
```{r FIGURE FORMATTING: EMOTIONAL EXPERIENCE}
# Add the beta-coefficients and error bars to the graph.
figure_emotional_experience <- ggplot(data_emotional_experience, aes(x=Coefficient, y=Outcome, color = Color)) + # Define dataset, x, y and color variables.
  geom_point(size=8, show.legend = FALSE) + # Create points on the graph for the beta-coefficients. define the size of the point as 8.
  geom_errorbarh(aes(y=Outcome, xmin=Lower_CI_90, xmax=Upper_CI_90, color = Color), # Create error bars for the 90% confidence interval.
                 linewidth=2, height = 0, show.legend = FALSE) + # Define line width as 2 and height as 0 (this ensures that the error bar is just a line with no end bars).
  geom_errorbarh(aes(y=Outcome, xmin=Lower_CI_95, xmax=Upper_CI_95, color = Color), # Create error bars for the 95% confidence interval.
                 linewidth=1, height=0, show.legend = FALSE, lineend = "round") # Define line width as 1 and height as 0 (this ensures that the error bar is just a line with no end bars).
  
# Add a dotted vertical line at 0.
figure_emotional_experience <- figure_emotional_experience +
  geom_vline(xintercept=0, linetype="dotted", size=2) 

# Change the background colors of the graph.
figure_emotional_experience <- figure_emotional_experience +
  theme_minimal() # Change the background of the graph to be white with grey grid lines.

# Y-Axis
figure_emotional_experience <- figure_emotional_experience +
  scale_y_discrete(limits = rev(c("Positive emotional index", # Fix the order of the outcomes.
                      "Negative emotional index", 
                      "Composite emotional index")),
                   labels = function(x) str_wrap(x, width = 20)) + # Condense the size of the outcome labels, so that they are split in 2-3 lines.
  ylab("Emotional\nExperience") + # Title the y-axis with the outcome group ("Emotional Experience").
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 95, b = 0, l = 0), # Define the size of the margins of the y-axis title (t = top, r = right, b = bottom, l = left).
                                    size=24, face="bold"), # Define the text size as 24, and bold the text.
        axis.text.y = element_text(margin = margin(t = 0, r = 80, b = 0, l = 0), # Define the size of the margins of the outcome labels (t = top, r = right, b = bottom, l = left).
                                   size=14, hjust = 0.5), # Define the text size as 14, and center the text.
        text = element_text(family="Verdana")) # Define the text font as "Verdana".

# X-axis.
figure_emotional_experience <- figure_emotional_experience + 
  scale_x_continuous(labels=NULL, limits = c(-0.26, 0.26)) + # Get rid of the x-axis labels (this is important for when the figures are stitched together), limit the x-axis between the range of -0.26 to 0.26.
  xlab(NULL) # Get rid of x-axis title.

# Colors.
figure_emotional_experience <- figure_emotional_experience + 
  scale_color_identity()  # Ensure the colors of the points/bars are in accordance with the significance colors stated in the dataframe.
  
# Final emotional experience outcomes plot.
print(figure_emotional_experience)
```

# FIGURE FORMATTING: POLITICAL ATTITUDES.
```{r FIGURE FORMATTING: POLITICAL ATTITUDES}
# Add the beta-coefficients and error bars to the graph.
figure_political_attitudes <- ggplot(data_political_attitudes, aes(x=Coefficient, y=Outcome, color = Color)) + # Define dataset, x, y and color variables.
  geom_point(size=8, show.legend = FALSE) + # Create points on the graph for the beta-coefficients. define the size of the point as 8.
  geom_errorbarh(aes(y=Outcome, xmin=Lower_CI_90, xmax=Upper_CI_90, color = Color), # Create error bars for the 90% confidence interval.
                 linewidth=2, height = 0, show.legend = FALSE) + # Define line width as 2 and height as 0 (this ensures that the error bar is just a line with no end bars).
  geom_errorbarh(aes(y=Outcome, xmin=Lower_CI_95, xmax=Upper_CI_95, color = Color), # Create error bars for the 95% confidence interval.
                 linewidth=1, height=0, show.legend = FALSE, lineend = "round") # Define line width as 1 and height as 0 (this ensures that the error bar is just a line with no end bars).
  
# Add a dotted vertical line at 0.
figure_political_attitudes <- figure_political_attitudes +
  geom_vline(xintercept=0, linetype="dotted", size=2)  

# Change the background colors of the graph.
figure_political_attitudes <- figure_political_attitudes +
  theme_minimal() # Change the background of the graph to be white with grey grid lines.

# Y-Axis.
figure_political_attitudes <- figure_political_attitudes +
  scale_y_discrete(limits = rev(c("Change in affective polarization", # Fix the order of the outcomes.
                      "Moderation of focal policy position")),
                   labels = function(x) str_wrap(x, width = 20)) + # Condense the size of the outcome labels, so that they are split in 2-3 lines.
  ylab("Political\nAttitudes") + # Title the y-axis with the outcome group ("Political Attitudes").
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 95, b = 0, l = 0), # Define the size of the margins of the y-axis title (t = top, r = right, b = bottom, l = left).
                                    size=24, face="bold"), # Define the text size as 24, and bold the text.
        axis.text.y = element_text(margin = margin(t = 0, r = 80, b = 0, l = 0), # Define the size of the margins of the outcome labels (t = top, r = right, b = bottom, l = left).
                                   size=14, hjust = 0.5), # Define the text size as 14, and center the text.
        text = element_text(family="Verdana")) # Define the text font as "Verdana".

# X-axis.
figure_political_attitudes <- figure_political_attitudes + 
  scale_x_continuous(limits = c(-0.26, 0.26)) + # Get rid of the x-axis labels (this is important for when the figures are stitched together), limit the x-axis between the range of -0.26 to 0.26.
  xlab("Treatment effect (in SDs)") + # Since this plot will be the last one to be stitched together, include the x-axis label "Treatment effect (in SDs)".
  theme(axis.title.x = element_text(margin=margin(t = 25, r = 0, b = 0, l = 0), # Define the size of the margins of the x-axis title (t = top, r = right, b = bottom, l = left).
                                    size=18, face="bold"), # Define the text size as 18, and bold the text.
        text = element_text(family="Verdana")) # Define the text font as "Verdana".

# Colors.
figure_political_attitudes <- figure_political_attitudes + 
  scale_color_identity()  # ensure the colors of the points/bars are in accordance with the significance colors stated in the dataframe.
  
# Final political attitudes outcomes plot.
print(figure_political_attitudes)
```

# COMBINE INTELLECTUAL HUMILITY, EMOTIONAL EXPERIENCE, AND POLITICAL ATTITUDES FIGURES INTO FINAL FIGURE.
```{r COMBINE INTELLECTUAL HUMILITY, EMOTIONAL EXPERIENCE, AND POLITICAL ATTITUDES FIGURES INTO FINAL FIGURE}
# Combine the intellectual humility, emotional experience, and political attitudes plot together into the final figure three.
figure_3 <- ggarrange(figure_intellectual_humility, figure_emotional_experience, figure_political_attitudes, ncol=1, heights = c(3.5,3.5,3), align = "v") # align the three plots vertically ("v") and define the heights as 3.5, 3.5, 3, respectively.
```

# FINAL FIGURE.
```{r FINAL FIGURE}
print(figure_3)
```

# REMOVE EXTRA DATAFRAMES AND VALUES FROM ENVIRONMENT.
```{r REMOVE EXTRA DATAFRAMES AND VALUES FROM ENVIRONMENT}
# Remove extra dataframes and values from environment.
# rm(list=ls())
```

