---
title: "SI.Section.13"
author: "Austin van Loon and Srikar Katta"
date: "`r Sys.Date()`"
output: 
  rmdformats::readthedown
---

# LOADING PACKAGES.
```{r setup, include=FALSE}
rm(list = ls())
library(tidyverse)

theme_set(theme_bw() + theme(text = element_text(size = 15)))
knitr::opts_chunk$set(echo = TRUE)
```

# LOAD IN DATA.
```{r LOAD IN DATA}
# Create dataframe "data_with_pure_control" which contains cleaned participant data with pure controls.
data_with_pure_control <- read_csv('../Data/data_with_pure_control_cleaned.csv') # Read csv data file.

# Create dataframe "linguistic_humility_data" which contains linguistic humility scores for all participants (including pure controls).
linguistic_humility_data <- read_csv('../Data/timestamped_perspective_scores_all.csv')
```

# STANDARDIZE VARIABLES.
```{r STANDARDIZE VARIABLES}
# Standardize curiosity score in linguistic_humility_data.
linguistic_humility_data <- linguistic_humility_data %>% 
  mutate(CURIOSITY_EXPERIMENTAL = scale(CURIOSITY_EXPERIMENTAL))

# Standardize respect score in linguistic_humility_data.
linguistic_humility_data <- linguistic_humility_data %>% 
  mutate(RESPECT_EXPERIMENTAL = scale(RESPECT_EXPERIMENTAL))

# Standardize nuance score in linguistic_humility_data.
linguistic_humility_data <- linguistic_humility_data %>% 
  mutate(NUANCE_EXPERIMENTAL = scale(NUANCE_EXPERIMENTAL))

# Standardize ih_engagement in data_with_pure_control.
data_with_pure_control <- data_with_pure_control %>% 
  mutate(ih_engagement = scale(ih_engagement))

# Standardize delta_ih in data_with_pure_control.
data_with_pure_control <- data_with_pure_control %>% 
  mutate(delta_ih = scale(delta_ih))

# Standardize delta_ih items 1-6 in data_with_pure_control.
data_with_pure_control <- data_with_pure_control %>% 
  mutate(delta_ih_1 = scale(delta_ih_1)) %>% # Item 1.
  mutate(delta_ih_2 = scale(delta_ih_2)) %>% # Item 2.
  mutate(delta_ih_3 = scale(delta_ih_3)) %>% # Item 3. 
  mutate(delta_ih_4 = scale(delta_ih_4)) %>% # Item 4. 
  mutate(delta_ih_5 = scale(delta_ih_5)) %>% # Item 5. 
  mutate(delta_ih_6 = scale(delta_ih_6)) # Item 6. 
  
# Standardize panas_pos in data_with_pure_control.
data_with_pure_control <- data_with_pure_control %>% 
  mutate(panas_pos = scale(panas_pos))

# Standardize panas_neg in data_with_pure_control.
data_with_pure_control <- data_with_pure_control %>% 
  mutate(panas_neg = scale(panas_neg))  

# Standardize panas in data_with_pure_control.
data_with_pure_control <- data_with_pure_control %>% 
  mutate(panas = scale(panas))  

# Standardize affective_polarization in data_with_pure_control.
data_with_pure_control <- data_with_pure_control %>% 
  mutate(affective_polarization = scale(affective_polarization))  

# Standardize extremity_post_less_pre in data_with_pure_control.
data_with_pure_control <- data_with_pure_control %>% 
  mutate(extremity_post_less_pre = scale(extremity_post_less_pre))  
```

# SPECIFY "CONDITION" COLUMN FACTOR LEVEL.
```{r SPECIFY "CONDITION" COLUMN FACTOR LEVEL}
# Specify factor order of "condition" column. This is important for when analyses are run (e.g., t-value valence, etc.).
data_with_pure_control$condition <- factor(data_with_pure_control$condition, levels = c("treat", "control", "pure_control")) # Levels are now in the order of: treatment, control, pure_control.
```

# PURE CONTROL ARM ANALYSES - AUTHORING INTELLECTUALLY HUMBLE CONTENT.
```{r PURE CONTROL ARM ANALYSES - AUTHORING INTELLECTUALLY HUMBLE CONTENT}
# The dataframe "data_with_pure_control" contains the experimental arm that each participant was assigned to (treatment, control, pure control). Classify participants in the "linguistic_humility_data" dataframe based on the experimental arm they were assigned to in "data_with_pure_control". 
linguistic_humility_data <- linguistic_humility_data %>%
  left_join(data_with_pure_control %>% # Join the "data_with_pure_control" dataframe to the "linguistic_humility_data" dataframe.
              select(participant_code, condition), # Select the participant_code and condition columns from data_with_pure_control.
              by = c('participantCode' = 'participant_code')) # Match the observations in "linguistic_humility_data" and "data_with_pure_control" by participant codes (participantCode in linguistic_humility_data and participant_code in data_with_pure_control).

# In the linguistic_humility_data dataframe, create column "linguistic_humility" which averages curiosity, respect, and nuance scores.
linguistic_humility_data <- linguistic_humility_data %>% 
  rowwise() %>% # Calculate the average for each row (1 row = 1 participant).
  mutate(linguistic_humility = mean(c(CURIOSITY_EXPERIMENTAL, RESPECT_EXPERIMENTAL, NUANCE_EXPERIMENTAL))) # Calculate the mean of curiosity, respect, and nuance scores.

# Specify factor order of the "condition" column in linguistic_humility_data.
linguistic_humility_data$condition <- factor(linguistic_humility_data$condition, levels = c("treat", "control", "pure_control")) # Levels are now in the order of: treatment, control, pure_control.

# Run an ANOVA, comparing intellectually humble authored content across the three conditions (treatment, control, pure control). Save as anova_linguistic_humility.
anova_linguistic_humility <- summary(aov(data = linguistic_humility_data,
                                         linguistic_humility ~ condition))

# Print the p-value.
print(anova_linguistic_humility[[1]][5])
```

# PURE CONTROL ARM ANALYSES - ENGAGMENT WITH INTELLECTUALLY HUMBLE CONTENT.
```{r PURE CONTROL ARM ANALYSES - ENGAGMENT WITH INTELLECTUALLY HUMBLE CONTENT}
# Run an ANOVA, comparing engagement with intellectually humble content across the three conditions (treatment, control, pure control). Save as anova_ih_engagement.
anova_ih_engagement <- summary(aov(data = data_with_pure_control, 
      ih_engagement ~ condition)) 

# Print the p-value.
print(anova_ih_engagement[[1]][5])
```

# PURE CONTROL ARM ANALYSES - SCORES ON SELF-REPORTED INTELLECTUAL HUMILITY SCALE.
```{r PURE CONTROL ARM ANALYSES - SCORES ON SELF-REPORTED INTELLECTUAL HUMILITY SCALE}
# Create dataframe "data_delta_ih" which excludes the participant who didn't answer all of the intellectual humility measures.
data_delta_ih <- data_with_pure_control[data_with_pure_control$participant_code != "9paveb", ]

# Specify factor order of "condition" column. This is important for when analyses are run (e.g., t-value valence, etc.).
data_delta_ih$condition <- factor(data_delta_ih$condition, levels = c("treat", "control", "pure_control")) # Levels are now in the order of: treatment, control, pure_control.

# Run an ANOVA, comparing scores on a self-reported intellectual humility scale across the three conditions (treatment, control, pure control). Save as anova_delta_ih.
anova_delta_ih <- summary(aov(data = data_delta_ih, 
      delta_ih ~ condition)) 

# Print the p-value.
print(anova_delta_ih[[1]][5])
```

# PURE CONTROL ARM ANALYSES - INDEX ITEM SCORES ON SELF-REPORTED INTELLECTUAL HUMILITY SCALE.
```{r PURE CONTROL ARM ANALYSES - INDEX ITEM SCORES ON SELF-REPORTED INTELLECTUAL HUMILITY SCALE}
# Create dataframe "data_delta_ih" which excludes the participant who didn't answer all of the intellectual humility measures.
data_delta_ih <- data_with_pure_control[data_with_pure_control$participant_code != "9paveb", ]

# Specify factor order of "condition" column. This is important for when analyses are run (e.g., t-value valence, etc.).
data_delta_ih$condition <- factor(data_delta_ih$condition, levels = c("treat", "control", "pure_control")) # Levels are now in the order of: treatment, control, pure_control.

###############INDEX ITEM ONE###############

# Run an ANOVA, comparing scores on index item one of a self-reported intellectual humility scale across the three conditions (treatment, control, pure control). Save as anova_delta_ih_1.
anova_delta_ih_1 <- summary(aov(data = data_delta_ih, 
      delta_ih_1 ~ condition))

# Print the p-value.
print(anova_delta_ih_1[[1]][5])

###############INDEX ITEM TWO###############

# Run an ANOVA, comparing scores on index item two of a self-reported intellectual humility scale across the three conditions (treatment, control, pure control). Save as anova_delta_ih_2.
anova_delta_ih_2 <- summary(aov(data = data_delta_ih, 
      delta_ih_2 ~ condition)) 

# Print the p-value.
print(anova_delta_ih_2[[1]][5])

###############INDEX ITEM THREE###############

# Run an ANOVA, comparing scores on index item three of a self-reported intellectual humility scale across the three conditions (treatment, control, pure control). Save as anova_delta_ih_3.
anova_delta_ih_3 <- summary(aov(data = data_delta_ih,
      delta_ih_3 ~ condition))

# Print the p-value.
print(anova_delta_ih_3[[1]][5])

###############INDEX ITEM FOUR###############

# Run an ANOVA, comparing scores on index item four of a self-reported intellectual humility scale across the three conditions (treatment, control, pure control). Save as anova_delta_ih_4.
anova_delta_ih_4 <- summary(aov(data = data_delta_ih,
      delta_ih_4 ~ condition))

# Print the p-value.
print(anova_delta_ih_4[[1]][5])

###############INDEX ITEM FIVE###############

# Run an ANOVA, comparing scores on index item five of a self-reported intellectual humility scale across the three conditions (treatment, control, pure control). Save as anova_delta_ih_5.
anova_delta_ih_5 <- summary(aov(data = data_delta_ih, 
      delta_ih_5 ~ condition))

# Print the p-value.
print(anova_delta_ih_5[[1]][5])

###############INDEX ITEM SIX###############

# Run an ANOVA, comparing scores on index item six of a self-reported intellectual humility scale across the three conditions (treatment, control, pure control). Save as anova_delta_ih_6.
anova_delta_ih_6 <- summary(aov(data = data_delta_ih,
      delta_ih_6 ~ condition))

# Print the p-value.
print(anova_delta_ih_6[[1]][5])
```

# PURE CONTROL ARM ANALYSES - POSITIVE EMOTIONS.
```{r PURE CONTROL ARM ANALYSES - POSITIVE EMOTIONS}
# Run an ANOVA, comparing scores on the panas positive emotions scale across the three conditions (treatment, control, pure control). Save as anova_panas_pos.
anova_panas_pos <- summary(aov(data = data_with_pure_control, 
      panas_pos ~ condition))

# Print the p-value.
print(anova_panas_pos[[1]][5])
```

# PURE CONTROL ARM ANALYSES - NEGATIVE EMOTIONS.
```{r PURE CONTROL ARM ANALYSES - NEGATIVE EMOTIONS}
# Run an ANOVA, comparing scores on the panas negative emotions scale across the three conditions (treatment, control, pure control). Save as anova_panas_neg.
anova_panas_neg <- summary(aov(data = data_with_pure_control,  
      panas_neg ~ condition))

# Print the p-value.
print(anova_panas_neg[[1]][5])
```

# PURE CONTROL ARM ANALYSES - COMPOSITE OF THE OVERALL QUALITY OF EMOTIONAL EXPERIENCE.
```{r PURE CONTROL ARM ANALYSES - COMPOSITE OF THE OVERALL QUALITY OF EMOTIONAL EXPERIENCE}
# Run an ANOVA, comparing overall scores on the panas emotions scale across the three conditions (treatment, control, pure control). Save as anova_panas.
anova_panas <- summary(aov(data = data_with_pure_control, 
      panas ~ condition)) 

# Print the p-value.
print(anova_panas[[1]][5])
```

# PURE CONTROL ARM ANALYSES - AFFECTIVE POLARIZATION.
```{r PURE CONTROL ARM ANALYSES - AFFECTIVE POLARIZATION}
# Create dataframe "data_no_true_independents" which exludes participants who identify as pure independents.
data_no_true_independents <- data_with_pure_control %>%
  filter(pid7 != "Pure Independent") # Filter out participants who identified as "Pure Independent".

# Specify factor order of "condition" column. This is important for when analyses are run (e.g., t-value valence, etc.).
data_no_true_independents$condition <- factor(data_no_true_independents$condition, levels = c("treat", "control", "pure_control")) # Levels are now in the order of: treatment, control, pure_control.

# Run an ANOVA, comparing affective polarization across the three conditions (treatment, control, pure control). Save as anova_affective_polarization.
anova_affective_polarization <- summary(aov(data = data_no_true_independents, 
      affective_polarization ~ condition))

# Print the p-value.
print(anova_affective_polarization[[1]][5])
```

# PURE CONTROL ARM ANALYSES - MODERATION OF BELIEFS ABOUT IMMIGRATION OR GUN CONTROL.
```{r PURE CONTROL ARM ANALYSES - MODERATION OF BELIEFS ABOUT IMMIGRATION OR GUN CONTROL}
# Run an ANOVA, comparing moderation of beliefs about immigration or gun control policies across the three conditions (treatment, control, pure control). Save as anova_extremity_post_less_pre.
anova_extremity_post_less_pre <- summary(aov(data = data_with_pure_control, 
      extremity_post_less_pre ~ condition)) 

# Print the p-value.
print(anova_extremity_post_less_pre[[1]][5])
```

