---
title: "SI.Section.5"
author: "Austin van Loon and Srikar Katta"
date: "`r Sys.Date()`"
output: 
  rmdformats::readthedown
---

# LOADING PACKAGES.
```{r setup, include=FALSE}
rm(list = ls())
library(tidyverse)
library(effsize)
library(ggplot2)

theme_set(theme_bw() + theme(text = element_text(size = 15)))
knitr::opts_chunk$set(echo = TRUE)
```

# LOAD IN DATA.
```{r LOAD IN DATA}
# Create dataframe "data" which contains cleaned participant data without pure controls.
data <- read_csv('../Data/data_cleaned.csv') # Read csv data file.
```

# SPECIFY "CONDITION" COLUMN FACTOR LEVEL.
```{r SPECIFY "CONDITION" COLUMN FACTOR LEVEL}
# Specify factor order of "condition" column. This is important for when analyses are run (e.g., t-value valence, etc.).
data$condition <- factor(data$condition, levels = c("treat", "control")) # Levels are now in the order of: treatment, control.
```

# TREATMENT ARM - AVERAGE WORDS PER POST, LIKES, DISLIKES.
```{r TREATMENT ARM - AVERAGE WORDS PER POST, LIKES, DISLIKES}
# Calculate the average words per post written by participants.
data %>%
  filter(condition == "treat") %>% # Filter for participants in the treatment condition.
  summarise(mean = sum(total_words_in_posts)/sum(num_posts)) %>% # Add the amount of words in all posts and divide by the total number of posts.
  mutate(mean = round(mean, 0)) # Round the mean to 0 decimal places.

# Calculate the average amount of likes.
data %>%
  filter(condition == "treat") %>% # Filter for participants in the treatment condition.
  summarise(mean = mean(total_likes)) %>% # Calculate the mean of the variable total_likes.
  mutate(mean = round(mean, 1)) # Round the mean to 1 decimal place.

# Calculate the average amount of dislikes.
data %>%
  filter(condition == "treat") %>% # Filter for participants in the treatment condition.
  summarise(mean = mean(total_dislikes)) %>% # Calculate the mean of the variable total_dislikes.
  mutate(mean = round(mean, 2)) # Round the mean to 2 decimal places.
```

# CONTROL ARM - AVERAGE WORDS PER POST, LIKES, DISLIKES.
```{r CONTROL ARM - AVERAGE WORDS PER POST, LIKES, DISLIKES}
# Calculate the average words per post written by participants.
data %>%
  filter(condition == "control") %>% # Filter for participants in the control condition.
  summarise(mean = sum(total_words_in_posts)/sum(num_posts)) %>% # Add the amount of words in all posts and divide by the total number of posts.
  mutate(mean = round(mean, 0)) # Round the mean to 0 decimal places.

# Calculate the average amount of likes.
data %>%
  filter(condition == "control") %>% # Filter for participants in the control condition.
  summarise(mean = mean(total_likes)) %>% # Calculate the mean of the variable total_likes.
  mutate(mean = round(mean, 1)) # Round the mean to 1 decimal place.

# Calculate the average amount of dislikes.
data %>%
  filter(condition == "control") %>% # Filter for participants in the control condition.
  summarise(mean = mean(total_dislikes)) %>% # Calculate the mean of the variable total_dislikes.
  mutate(mean = round(mean, 2)) # Round the mean to 0 decimal places.
```

# DIFFERENCE BETWEEN NUMBER OF POSTS LIKED/DISLIKED BETWEEN TREATMENT AND CONTROL.
```{r DIFFERENCE BETWEEN NUMBER OF POSTS LIKED/DISLIKED BETWEEN TREATMENT AND CONTROL}
###############COMPARING NUMBER OF LIKES###############

# Run a t-test, comparing (between conditions: treatment and control) the number of liked posts. Save as "t.test_likes".
t.test_likes <- t.test(data = data, total_likes ~ condition,
        alternative = 'two.sided',
        var.equal = TRUE) 

# Calculate the effect size (Cohen's d). Save in dataframe "d_likes".
d_likes <- effsize::cohen.d(data = data, total_likes ~ condition)

# Final formatting pasting results together.
paste0("d = ", round(d_likes$estimate,2), ",", " t = ", round(t.test_likes$statistic,2) , ",", " df = ", t.test_likes$parameter, ",", " P = ", round(t.test_likes$p.value,3))

###############COMPARING NUMBER OF DISLIKES###############

# Run a t-test, comparing (between conditions: treatment and control) the number of disliked posts. Save as "t.test_dislikes".
t.test_dislikes <- t.test(data = data, total_dislikes ~ condition,
        alternative = 'two.sided',
        var.equal = TRUE) 

# Calculate the effect size (Cohen's d). Save in dataframe "d_dislikes".
d_dislikes <- effsize::cohen.d(data = data, total_dislikes ~ condition)

# Final formatting pasting results together.
paste0("d = ", round(d_dislikes$estimate,2), ",", " t = ", round(t.test_dislikes$statistic,2) , ",", " df = ", t.test_dislikes$parameter, ",", " P = ", round(t.test_dislikes$p.value,3))

###############COMPARING NUMBER OF POOLED LIKES AND DISLIKES###############

# Create column "pooled_likes_dislikes" which calculates the sum of liked and disliked posts for each participant. 
data <- data %>% 
  mutate(pooled_likes_dislikes = total_likes + total_dislikes)

# Run a t-test, comparing (between conditions: treatment and control) the pooled number of liked and disliked posts. Save as "t.test_likes_and_dislikes".
t.test_likes_and_dislikes <- t.test(data = data, pooled_likes_dislikes ~ condition,
        alternative = 'two.sided',
        var.equal = TRUE)

# Calculate the effect size (Cohen's d). Save in dataframe "d_likes_and_dislikes".
d_likes_and_dislikes <- effsize::cohen.d(data = data, pooled_likes_dislikes ~ condition)

# Final formatting pasting results together.
paste0("d = ", round(d_likes_and_dislikes$estimate,2), ",", " t = ", round(t.test_likes_and_dislikes$statistic,2) , ",", " df = ", t.test_likes_and_dislikes$parameter, ",", " P = ", round(t.test_likes_and_dislikes$p.value,3))

```

# DIFFERENCE IN TEXT LENGTH BETWEEN TREATMENT AND CONTROL.
```{r DIFFERENCE IN TEXT LENGTH BETWEEN TREATMENT AND CONTROL}
###############COMPARING NUMBER OF WORDS WRITTEN IN POSTS###############

# Run a t-test, comparing (between conditions: treatment and control) the number of words in posts written by participants. Save in dataframe "t.test_post_words".
t.test_post_words <- t.test(data = data, total_words_in_posts ~ condition,
        alternative = 'two.sided',
        var.equal = TRUE)

# Calculate the effect size (Cohen's d). Save in dataframe "d_post_words".
d_post_words <- effsize::cohen.d(data = data, total_words_in_posts ~ condition)

# Final formatting pasting results together.
paste0("d = ", round(d_post_words$estimate,2), ",", " t = ", round(t.test_post_words$statistic,2) , ",", " df = ", t.test_post_words$parameter, ",", " P = ", round(t.test_post_words$p.value,3))

###############COMPARING NUMBER OF WORDS WRITTEN IN COMMENTS###############

# Run a t-test, comparing (between conditions: treatment and control) the number of words in comments written by participants. Save in dataframe "t.test_comments_words".
t.test_comments_words <- t.test(data = data, total_words_in_comments ~ condition,
        alternative = 'two.sided',
        var.equal = TRUE) 

# Calculate the effect size (Cohen's d). Save in dataframe "d_comments_words".
d_comments_words <- effsize::cohen.d(data = data, total_words_in_comments ~ condition)

# Final formatting pasting results together.
paste0("d = ", round(d_comments_words$estimate,2), ",", " t = ", round(t.test_comments_words$statistic,2) , ",", " df = ", t.test_comments_words$parameter, ",", " P = ", round(t.test_comments_words$p.value,3))

###############COMPARING NUMBER OF WORDS WRITTEN IN POSTS AND COMMENTS (POOLED)###############

# Run a t-test, comparing (between conditions: treatment and control) the pooled number of words in posts and comments written by participants. Save in dataframe "t.test_written_words".
t.test_written_words <- t.test(data = data, total_words_written ~ condition,
        alternative = 'two.sided',
        var.equal = TRUE)

# Calculate the effect size (Cohen's d). Save in dataframe "d_written_words".
d_written_words <- effsize::cohen.d(data = data, total_words_written ~ condition)

# Final formatting pasting results together.
paste0("d = ", round(d_written_words$estimate,2), ",", " t = ", round(t.test_written_words$statistic,2) , ",", " df = ", t.test_written_words$parameter, ",", " P = ", round(t.test_written_words$p.value,3))
```

# DISTRIBUTION OF BOT DETECTION.
```{r DISTRIBUTION OF BOT DETECTION}
# Create dataframe "control_bots" which calculates the proportion of bot detection in the control condition.
control_bots <- data %>% 
  filter(condition == "control") %>% # Filter for participants in the control condition.
  count(bots) %>% # Count the number of participants who selected each bot detection response.
  mutate(proportion = prop.table(n)*100) # Calculate the proportion of bot detection responses.

# Create column "Experimental Condition" which indicates the experimental condition.
control_bots <- control_bots %>% 
  mutate(`Experimental Condition` = "Control") # Experimental condition was control.

# Create dataframe "treatment_bots" which calculates the proportion of bot detection in the treatment condition.
treatment_bots <- data %>% 
  filter(condition == "treat") %>% # Filter for participants in the treatment condition.
  count(bots) %>% # Count the number of participants who selected each bot detection response.
  mutate(proportion = prop.table(n)*100) # Calculate the proportion of bot detection responses.

# Create column "Experimental Condition" which indicates the experimental condition.
treatment_bots <- treatment_bots %>% 
  mutate(`Experimental Condition` = "Treatment") # Experimental condition was treatment.

# Combine control_bots and treatment_bots into one dataframe "bot_detection".
bot_detection <- rbind(control_bots, treatment_bots)

# Create a bar chart which plots the proportion of bot detection responses in the control/treatment groups.
ggplot(data=bot_detection, aes(x = proportion, y = bots, fill = `Experimental Condition`)) + # Define dataset, x, y and fill variables.
  geom_bar(stat = "identity", position = "dodge") + # In the form of a bar chart, use the proportions defined in the dataset as the bar heights ("identity"), and stagger the bars ("dodge") so that treatment and control bars are next to each other.
  theme_minimal() + # Select a minimal background for the bar chart.
  ylab("Bots detected?") + # Label the y-axis.
  xlab("Proportion of participant responses (%)") # Label the x-axis.
```

# BELIEF IN NO BOTS, ONE OR FEWER BOTS.
```{r BELIEF IN NO BOTS, ONE OR FEWER BOTS}
# Create dataframe "bot_belief" which calculates the proportion of participants' bot detection responses.
bot_belief <- data %>% 
  count(bots) %>% # Count the number of participants who selected each bot detection response.
  mutate(proportion = prop.table(n)*100) # Calculate the proportion of bot detection responses.

# Identify the proportion of participants who believed they did not encounter bots.
bot_belief$proportion[bot_belief$bots == "No, I did not encounter any bots"]

# Calculate the proportion of participants who believed they encountered fewer than one or two bots.
bot_belief$proportion[bot_belief$bots == "No, I did not encounter any bots"] + bot_belief$proportion[bot_belief$bots == "Yes, I encountered one or two bots"]
```

# FUTURE PLATFORM USE.
```{r FUTURE PLATFORM USE}
# Create dataframe "future_platform_use" which calculates the proportion of participants' future platform use responses.
future_platform_use <- data %>% 
  count(future_use) %>% # Count the number of participants who selected each future use response.
  mutate(proportion = prop.table(n)*100) # Calculate the proportion of future use responses.

# Identify the proportion of participants who are at least somewhat likely to use the platform again.
future_platform_use$proportion[future_platform_use$future_use == "Somewhat likely"] + future_platform_use$proportion[future_platform_use$future_use == "Very likely"]
```
